\setsecnumdepth{subsubsection}
\settocdepth{subsubsection}

\chapter{Just Used 5 Minutes Translations}

%Put these here

\chapter{\textit{Your Name} (君の名は。) Translation}

\columnratio{0.2,0.8}
\begin{paracol}{2}
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{mi JasiT PRiiLli te?}}\\
`You got lost?'
\endpreamble
mi[\sc 2sg]
JasiT[way]
PRiiL[forget]@
-li[\sc -q]
te[\sc atl]@
\nogloss{?}
\glft
迷った？\\
You got lost?\\
\textit{Fór du vild?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{瀧としての三葉:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{ure.}}\\
`Yep.'
\endpreamble
ure[\sc cop]@
\nogloss{.}
\glft
うん\\
Yeah.\\
\textit{Ja.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{caa... liwsan iSKuLa-JasiT PRiiLli?}}\\
`Seriously...?! How did you forget the way to school?'
\endpreamble
caa[\sc atl]
liwsan[what:reason]
iSKuLa[school]@
-JasiT[-way]
PRiiL[forget]@
-li[\sc q]@
\nogloss{?}
\glft
お前さあ どうやったら 通学で道に迷えんだよ?\\
How could you get lost on the way to school?\\
\textit{Helt ærligt. Hvordan kan man glemme vejen til skole?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{瀧としての三葉:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{eee... PRaLnar---}}\\
`uh... sorry---'
\endpreamble
eee[um]@
\nogloss{...}
PRaL[forgotten]@
-nar[\sc -f:phat]
\glft
ああ えーと わたし…\\
Well... y'know... a girl like me...\\
\textit{Om forladelse.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{PRaLnar le?}}\\
`Huh? Sorry?'
\endpreamble
PRaL[forgotten]@
-nar[\sc -f:phat]
le[\sc atl]@
\nogloss{?}
\glft
わたし？\\
Girl?\\
\textit{Om forladelse?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{瀧としての三葉:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{PRaLunara?! ... PRaLjar? ... kud PRaL?}}\\
`Sorry?! ... Sorry? ... Sorry?'
\endpreamble
PRaL[forgotten]@
-un[\sc -f]@
-ara[\sc -phat]
\nogloss{...}
PRaL[forgotten]@
-jar[\sc -m:phat]
\nogloss{...}
kud[\sc phat]
PRaL[forgotten]
\glft
あっ わたくし …… 僕 …… 俺\\
A... a fella like me... ... Stud? ... Guy?\\
\textit{Beklager. ... Tilgiv mig. ... Undskyld.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{瀧としての三葉:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{kud PRaL, JaL nas JaBaja. \textrm{T}OKYO-PLaS JaS-NaM esk FaSore yii.}}\\
`Sorry, I was enjoying everything. Tokyo is lively like a holiday!'
\endpreamble
kud[\sc phat]
PRaL[forgotten]@
\nogloss{,}
JaL[all]
nas[\sc 1sg]
JaBa[good]@
-ja[\sc -exist]@
\nogloss{.}+
\textrm{T}OKYO[Tokyo]@
-PLaS[-place]
Jas-NaM[holiday]
esk[like]
FaSa[alive]@
-ure[\sc -cop]
yii[\sc atl]@
\nogloss{!}
\glft
あ… 俺 楽しかったんやよ。なんか毎日 お祭りみたい 東京って。\\
I reckon a guy like me's got to enjoy himself every now and again. It's so festive in Tokyo, y'know?\\
\textit{Undskyld, jeg hyggede mig bare. Det er så dejligt at være i Tokyo.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{liwsan mi MuNTaw-FaM FiiMli?}}\\
`Why are you speaking Western dialect?'
\endpreamble
liwsan[what:reason]
mi[\sc 2sg]
MuNTaw[west]@
-FaM[-speech]
FiiM[speak\textbackslash{\sc tr}]@
-li[\sc -q]@
\nogloss{?}
\glft
なんかお前 なまってない？\\
What's with the dialect?\\
\textit{Hvorfar taler du dialekt?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{藤井司:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{\textrm{T}AKI, mi NurMiilali? ... caa x...}}\\
`Taki, do you have any food? ... Tsk, seriously...?'
\endpreamble
\textrm{T}AKI[Taki]
mi[\sc 2sg]
NurMi[food]@
-ila[\sc -exist]@
-li[\sc -q]@
\nogloss{?}
\nogloss{...}
caa[\sc atl]
x[\sc atl]@
\nogloss{...}
\glft
瀧 弁当は？ まったく\\
Where's your lunch? Geez.\\
\textit{Har du ikke mad med? Du er håbløs.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{mi SiyaJe\lilglot{} hakli x?}}\\
`Are you still sleeping?'
\endpreamble
mi[\sc 2sg]
SiyaJ[sleep\textbackslash{\sc mid}]@
-e\lilglot{}[\sc -cvb]
hak[continue]@
-li[\sc -q]
x[\sc atl]@
\nogloss{?}
\glft
寝ぼけてんのか？\\
Feels like you're sleepwalking.\\
\textit{Halvsover du?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{藤井司:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{nemi lis YiiTli?}}\\
`What do we give?'
\endpreamble
nemi[\sc 2du.incl]
li[\sc q]@
-s[\sc -nmz]
YiiT[give]@
-li[\sc -q]@
\nogloss{?}
\glft
何かあるか？\\
Got anything?\\
\textit{Hvad skal vi give ham?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{FurSi-la KRurKTi hwaNaMauru.}}\\
`Egg and croquette should be tasty.'
\endpreamble
FurSi[egg]@
-la[\sc -com]
KRurKTi[croquette]
hwa-[\sc infr-]@
NaMa[tasty]@
-uru[\sc -cop]@
\nogloss{.}
\glft
卵コロッケサンドにしようぜ\\
Croquette-egg sandwich sounds good!\\
\textit{Æg og croquette er fint.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{瀧としての三葉:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{kud NaM.}}\\
`Thanks for the food.'
\endpreamble
kud[\sc phat]
NaM[food]
\glft
あ… ありがとう\\
Thank you.\\
\textit{Tusind tak.}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{高木真太:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{iSKuLa yin iQuFa PLiiSe\lilglot{} usnak.}}\\
`Let's go to a cafe after school.'
\endpreamble
iSKuLa[school]
yin[after]
iQuFa[coffee\textbackslash place]
PLiiS[go\_to]@
-e\lilglot{}[\sc -cvb]
usnak[\sc hort]@
\nogloss{.}
\glft
放課後 カフェ行かね？\\
Let's stop by that café.\\
\textit{Skal vi ikke tage på café?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{藤井司:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{pars? usnak. \textrm{T}AKI?}}\\
`That one? Let's. Taki?'
\endpreamble
par[\sc dem.med]@
-s[\sc -nmz]@
\nogloss{?}
usnak[\sc hort]@
\nogloss{.}
\textrm{T}AKI[Taki]@
\nogloss{?}
\glft
ああ，例の？ いいね。瀧は？\\
Oh yeah? Sure. Taki, you coming?\\
\textit{Den sædvanlige? Okay. Hvad med dig, Taki?}
\endgl
\xe

\bigskip
\switchcolumn*
\hfill \textbf{瀧としての三葉:}

\switchcolumn

\exdisplay[lingstyle=Conversation]
\begingl 
\glpreamble
\textbf{\famword{iQuFa yii?!}}\\
`A café?!'
\endpreamble
iQuFa[café]
yii[\sc atl]
\glft
え？ え！ えー！ カフェ!?\\
W-What? What!? A café!?\\
\textit{Café?}
\endgl
\xe

\end{paracol}

% \bigskip
% \switchcolumn*
% \hfill \textbf{name}

% \switchcolumn

% \exdisplay[lingstyle=Conversation]
% \begingl 
% \glpreamble
% \textbf{\famword{i}}\\
% `e'
% \endpreamble
% gloss[gloss]
% \glft
% ex
% \endgl
% \xe