\setsecnumdepth{part}
\settocdepth{section}

\chapter{Roots and Derived Words}
\begin{multicols*}{2}

%%%%%%%%%%%
%    7
%%%%%%%%%%%
\section*{\bigglot}

\begin{dictroot}{\bigglot}{\bigglot}\label{root:7_7}
    \begin{dictentry}{{\bigglot}a\bigglot}{n.}\label{word:7a7}
        \dictdef*{%
            stupidity
            \begin{quote}
                \famword{iRu\bigglot a fit ReTaSa \bigglot a\bigglot ila}\\
                \textit{`In the legislature, there's only stupidity.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{{\bigglot}ii\bigglot}{v.tr.}\label{word:7ii7}
        \dictdef*{%
            to fail to achieve \textit{smth.}, to miss attaining \textit{smth.}, to fall short of \textit{smth.}
            \begin{quote}
                \famword{iSKuLa wa RaT fit bar SKanaL \bigglot ii\bigglot}\\
                \textit{`Three kids flunked out of school this year.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{{\bigglot}iya{\bigglot}{}}{v.intr.}\label{word:7iya7}
        \dictdef*{%
            \textit{(of an attempt or instrument)} to fail, to be unsuccessful, to not succeed, to be found wanting
            \begin{quote}
                \famword{was wan TaTaBaT \bigglot iya\bigglot e7 lit}\\
                \textit{`His new idea failed spectacularly.'}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{i{\bigglot}aa\bigglot}{v.intr.}\label{word:i7aa7}
        \dictdef{%
            to behave stupidly, to act stupidly, to mess around
            \begin{quote}
                \famword{mi i\bigglot aa\bigglot e\lilglot tuuquc ManaM FiiM}\\
                \textit{`Mom says that you need to stop messing around.'}
            \end{quote}
        }
        \dictdef{%
            \textit{(of an agent)} to fail, to not achieve anything, to be fall short of the understood standard, to fuck up
            %\begin{quote}
                %pars 
            %\end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{{\bigglot}i{\bigglot}iya\bigglot}{v.tr.}\label{word:7i7iya7}
        \dictdef*{
            to cause \textit{smth.} to fail, to sabotage \textit{smth.}, to fuck with \textit{smth.}, to mess \textit{smth.} up
        }
    \end{dictentry}
    \begin{dictentry}{aa{\bigglot}i\bigglot}{v.tr.}\label{word:aa7i7}
        \dictdef{%
            to cause \textit{sme.} to act like an idiot, to goad \textit{sme.} on, to instigate \textit{sme.}
        }
        \dictdef{%
            to cause \textit{sme.} to fail, to sabotage \textit{sme.}, to trip \textit{sme.} up, to mess with \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{\bigglot{}a\bigglot{}a}{adj.}\label{word:7a7a}
        \dictdef*{
            stupid
        }
    \end{dictentry}
    \begin{dictentry}{\bigglot{}ana\bigglot}{n.}\label{word:7ana7}
        \dictdef{%
            stupid person, fool
        }
        \dictdef{%
            \textit{(archaic)} native Narelander, \lang{} speaker
        }
    \end{dictentry}
    \begin{dictentry}{i\bigglot u\bigglot a}{n.}\label{word:i7u7a}
        \dictdef{%
            Nareland, an island to the northwest of Scotland, home of the Narelanders
        }
        \dictdef{%
            \textit{(meta, joke)} the CDN
        }
    \end{dictentry}
    \begin{dictentry}{\bigglot uu\bigglot}{n.}\label{word:7uu7}
        \dictdef*{\textit{(archaic)} Narelanders, the ethnic group descended from the pre-Indo-European inhabitants of Nareland}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{\bigglot}{j}\label{root:7_J}
    % aunt/uncle-niece/nephew (close)
    \begin{dictentry}{{\bigglot}anaJ}{n.}\label{word:7anaJ}
        \dictdef{
            parent's sibling, aunt, uncle
        }
        \dictdef{
            sibling's child, niece, nephew
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    B
%%%%%%%%%%%
\section*{B}

\begin{dictroot}{b}{\bigglot}\label{root:B_7}
    % sibling (close)
    \begin{dictentry}{Bana\bigglot}{n.}\label{word:Bana7}
        \dictdef*{
            sibling, sister, brother, cousin
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{b}\label{root:B_B}
    % so-so, quiet, light, not intense
    \begin{dictentry}{BaB}{n.}\label{word:BaB}
        \dictdef{
            simplicity
        }
        \dictdef{
            softness
        }
        \dictdef{
            silence
        }
        \dictdef{
            unobtrusiveness
        }
    \end{dictentry}
    \begin{dictentry}{BiiB}{v.tr}\label{word:BiiB}
        \dictdef{
            to hug \textit{sme.}
        }
        \dictdef{
            to squeeze \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{BiyaB}{v.intr.}\label{word:BiyaB}
        \dictdef*{
            \textit{of a task} to be performed or finished simply, easily, effortlessly
        }
    \end{dictentry}
    \begin{dictentry}{iBaaB}{v.intr.}\label{word:iBaaB}
        \dictdef{
            to behave oneself, keep quiet
        }
        \dictdef{
            to stay out of the way, not be a nuisance
        }
    \end{dictentry}
    \begin{dictentry}{BiBiyaB}{v.tr.}\label{word:BiBiyaB}
        \dictdef*{
            to perform a task effortlessly, easily
        }
    \end{dictentry}
    \begin{dictentry}{aaBiB}{v.tr.}\label{word:aaBiB}
        \dictdef*{
            to raise, nurture, care for, rear
        }
    \end{dictentry}
    \begin{dictentry}{BaBa}{adj.}\label{word:BaBa}
        \dictdef{
            soft, not hard, not rough
        }
        \dictdef{
            quiet, muffled
        }
        \dictdef{
            inoffensive, plain
        }
        \dictdef{
            easy, trivial
        }
        \dictdef{
            sensitive, gentle, with a light touch
        }
    \end{dictentry}
    \begin{dictentry}{BanaB}{n.}\label{word:BanaB}
        \dictdef{
            affectionate person, caring person
        }
        \dictdef{
            ragdoll
        }
    \end{dictentry}
    \begin{dictentry}{mBiB}{n.}\label{word:mBiB}
        \dictdef{
            fabric softener
        }
        \dictdef{
            exhaust muffler
        }
    \end{dictentry}
    \begin{dictentry}{BuBi}{n., adj.}\label{word:BuBi}
        \dictdef*{
            pink, the color pink
        }
    \end{dictentry}
    \begin{dictentry}{BuliB}{v.tr.}\label{word:BuliB}
        \dictdef*{
            the human breast
        }
    \end{dictentry}
    \begin{dictentry}{BuBu}{n.}\label{word:BuBu}
        \dictdef*{
            stuffed animal, teddy bear
        }
    \end{dictentry}
    \begin{dictentry}{BajuBa}{n.}\label{word:BajuBa}
        \dictdef*{
            a soft blanket, commonly used to 
        }
    \end{dictentry}
    \begin{dictentry}{BimiBu}{n.}\label{word:BimiBu}
        \dictdef*{
            bra, brassiere, undergarment worn to support the breasts 
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{BaBainala}{v.tr.}\label{word:BaBainala}
        \dictdef{
            to muffle, shush, quiet
        }
        \dictdef{
            to simplify
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{c}\label{root:B_C}
    % small, few
    \begin{dictentry}{BaCa}{adj.}\label{word:BaCa}
        \dictdef{
            small
        }
        \dictdef{
            few, small number of
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{j}\label{root:B_J}
    \begin{dictentry}{BaJ}{n.}\label{word:BaJ}
        \dictdef*{
            badness, evil, bad luck, bad fortune, bad vibes
        }
    \end{dictentry}
    \begin{dictentry}{BiiY}{v.tr.}\label{word:BiiY}
        \dictdef*{
            to treat \textit{sme.} badly, to screw \textit{sme.} over, to behave badly towards \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{BiyaJ}{v.intr.}\label{word:BiyaJ}
        \dictdef*{
            to have bad luck, to experience poor fortune, to be cursed
        }
    \end{dictentry}
    \begin{dictentry}{iBaaJ}{v.intr.}\label{word:iBaaJ}
        \dictdef*{
            to do evil, to do bad deeds, to behave badly, to misbehave
        }
    \end{dictentry}
    \begin{dictentry}{BiBiyaJ}{v.tr.}\label{word:BiBiyaJ}
        \dictdef*{
            to curse \textit{sme.}, to bestow bad luck upon \textit{sme.}, to give \textit{sme.} a curse
        }
    \end{dictentry}
    \begin{dictentry}{aaBiY}{v.tr.}\label{word:aaBiY}
        \dictdef*{
            to cause \textit{sme.} to behave badly, to instigate \textit{sme.}, to influence \textit{sme.} towards evil, to corrupt \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{BaJa}{adj.}\label{word:BaJa}
        \dictdef*{
            bad, unpleasant, unlucky, unfortunate
        }
    \end{dictentry}
    \begin{dictentry}{uBiJi}{adj.}\label{word:uBiJi}
        \dictdef*{
            unhappy, upset
        }
    \end{dictentry}
    \begin{dictentry}{BanaJ}{n.}\label{word:BanaJ}
        \dictdef{
            evildoer, bad person, villain
        }
        \dictdef{
            enemy, nemesis
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{n}\label{root:B_N}
    \begin{dictentry}{BaN}{n.}\label{word:BaN}
        \dictdef*{
            habit, routine
        }
    \end{dictentry}
    \begin{dictentry}{BiiN}{v.tr.}\label{word:BiiN}
        \dictdef*{
            to keep \textit{smth.} as a habit, to do \textit{smth.} usually, to have \textit{smth.} as a routine
        }
    \end{dictentry}
    \begin{dictentry}{BiyaN}{v.intr.}\label{word:BiyaN}
        \dictdef*{
            to be usual, to be typical practice, to be accepted as normal routine
        }
    \end{dictentry}
    \begin{dictentry}{iBaaN}{v.intr.}\label{word:iBaaN}
        \dictdef*{
            to behave as usual, to go about one's daily business, to do one's usual tasks
            }
    \end{dictentry}
    \begin{dictentry}{BiBiyaN}{v.tr.}\label{word:BiBiyaN}
        \dictdef*{
            to mandate \textit{smth.}, to put \textit{smth.} into practice, to make \textit{smth.} part of the day-to-day routine, to establish \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaBiN}{v.tr.}\label{word:aaBiN}
        \dictdef*{
            to train \textit{smth./sme.}, to habituate \textit{sme.} to something, to familiarize \textit{sme.} with something
        }
    \end{dictentry}
    \begin{dictentry}{BaNa}{adj.}\label{word:BaNa}
        \dictdef*{
            usual, common, ordinary, typical, banal, everyday, day-to-day
        }
    \end{dictentry}
    \begin{dictentry}{uBiNi}{adj.}\label{word:uBiNi}
        \dictdef*{
            bored, dissatisfied, exhausted, sick of the humdrum day-to-day grind
        }
    \end{dictentry}
    \begin{dictentry}{BuNi}{adj., n.}\label{word:BuNi}
        \dictdef*{
            yellow, the color yellow
        }
    \end{dictentry}
    \begin{dictentry}{BasiN}{n.}\label{word:BasiN}
        \dictdef*{
            banana
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{BaNiri}{v.intr.}\label{word:BaNiri}
        \dictdef{
            to do routine tasks, to do one's routine
        }
        \dictdef{
            \textit{(euphemistic)} to use the restroom, to take a piss
        }
    \end{dictentry}
    \begin{dictentry}{uBiNiisa}{n.}\label{word:uBiNiisa}
        \dictdef*{
            boredom, dissatisfaction, ennui
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{rb}\label{root:B_RB}
    %to leave (expecting to return), to brb
    \begin{dictentry}{BiyaRB}{v.intr.}\label{word:BiyaRB}
        \dictdef*{
            to be on hiatus, to be gone but expected to return shortly
        }
    \end{dictentry}
    \begin{dictentry}{iBaaRB}{v.intr.}\label{word:iBaaRB}
        \dictdef*{
            to leave expecting to return shortly
        }
    \end{dictentry}
    \dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{BaRBanara}{int.}\label{word:BaRBanara}
        \dictdef*{be right back, see you soon, goodbye (when the speaker expects to see the addresse again before either of them has a night's sleep)}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{rd}\label{root:B_RD}
    %bird
    \begin{dictentry}{BaRD}{n.}\label{word:BaRD}
        \dictdef*{
            flight
        }
    \end{dictentry}
    \begin{dictentry}{BiiRD}{v.tr}\label{word:BiiRD}
        \dictdef{
            to fly to \textit{smwh.}
        }
        \dictdef{
            \textit{(of a projectile like a bullet or arrow)} to hit \textit{smth. or sme.}
        }
    \end{dictentry}
    \begin{dictentry}{BiyaRD}{v.intr.}\label{word:BiyaRD}
        \dictdef{
            to fly, to be a passenger on a plane
        }
        \dictdef{
            to fly due to inertia, to fly through the air not of one's own power
        }
    \end{dictentry}
    \begin{dictentry}{iBaaRD}{v.intr}\label{word:iBaaRD}
        \dictdef*{
            to fly, to fly around
        }
    \end{dictentry}
    \begin{dictentry}{BiBiyaRD}{v.tr.}\label{word:BiBiyaRD}
        \dictdef{
            to throw \textit{smth.}, to launch \textit{smth.}, to shoot \textit{smth.}, to toss into the air
        }
        \dictdef{
            to shoot or launch a projectile \textit{(as from a gun, catapult, or cannon)}
        }
    \end{dictentry}
    \begin{dictentry}{aaBiRD}{v.tr.}\label{word:aaBiRD}
        \dictdef{
            to pilot \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{BaRDa}{adj.}\label{word:BaRDa}
        \dictdef{
            airborne
        }
        \dictdef{
            light, weightless
        }
    \end{dictentry}
    \begin{dictentry}{BanaRD}{n.}\label{word:BanaRD}
        \dictdef{
            acrobat, trapeze artist, tumbler, gymnast
        }
    \end{dictentry}
    \begin{dictentry}{BuRDi}{n.}\label{word:BuRDi}
        \dictdef*{
            bullet, cannonball, projectile
        }
    \end{dictentry}
    \begin{dictentry}{iBuRDa}{n.}\label{word:iBuRDa}
        \dictdef*{
            airport
        }
    \end{dictentry}
    \begin{dictentry}{mBiRD}{n.}\label{word:mBiRD}
        \dictdef{
            bow, catapult, trebuchet, slingshot, gun, any machine designed to launch a projectile
        }
        \dictdef{
            the engine of a plane, that which propels something to fly
        }
    \end{dictentry}
    \begin{dictentry}{BuliRD}{n.}\label{word:BuliRD}
        \dictdef{
            wing, a bird's wing
        }
    \end{dictentry}
    \begin{dictentry}{BuRDu}{n.}\label{word:BuRDu}
        \dictdef{
            bird
        }
        \dictdef{
            plane, airplane
        }
    \end{dictentry}
    \begin{dictentry}{BasiRD}{n.}\label{word:BasiRD}
        \dictdef{
            arrow, bolt, long thin projectile
        }
    \end{dictentry}
    \begin{dictentry}{BajuRDa}{n.}\label{word:BajuRDa}
        \dictdef{
            wing, the wing of a plane or glider
        }
        \dictdef{
            kite
        }
    \end{dictentry}
    \begin{dictentry}{aBiRDu}{n.}\label{word:aBiRDu}
        \dictdef*{
            bird's nest
        }
    \end{dictentry}
    \begin{dictentry}{BimiRDu}{n.}\label{word:BimiRDu}
        \dictdef{
            cage, bird cage
        }
    \end{dictentry}
    \dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{aaBiRDana}{n.}\label{word:aaBiRDana}
        \dictdef{
            pilot, someone who flies a plane
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{b}{t}\label{root:B_T}
    \begin{dictentry}{BaT}{n.}\label{word:BaT}
        \dictdef*{
            knowledge, understanding
            \begin{quote}
                \famword{wa aKiJu fit JaLa BaTila.} \\
                \textit{`There's much knowledge in these books.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{BiiT}{v.tr.}\label{word:BiiT}
        \dictdef{%
            to know \textit{smth.}, to understand \textit{smth.}
            \begin{quote}
                \famword{mi iBaaRBe\lilglot{} kajuc nas BiiT}\\
                \textit{`I know that you want to leave.'}
            \end{quote}
            }
        \dictdef{%
        to love \textit{sme.} like a brother, to have a close platonic bond with \textit{sme.}, to be best friends with \textit{sme.}
            \begin{quote}
                \famword{nas JanaB BiiTibi}\\
                \textit{`I love my friends.'}
            \end{quote}
        \textit{NB: the subject is reversed from its use as `to understand': \emph{\famword{mi nas BiiTibi}} means `you understand me' but `I love you' (platonically).}
            }
    \end{dictentry}
    \begin{dictentry}{BiyaT}{v.intr.}\label{word:BiyaT}
        \dictdef*{
            to be known, to be understood, to be a given, to be common sense, to be obvious
        }
    \end{dictentry}
    \begin{dictentry}{iBaaT}{v.intr.}\label{word:iBaaT}
        \dictdef{%
        to know, to understand, to be in a state of knowing or understanding what is going on
        }
        \dictdef{%
        \textit{(when used reciprocally)} to love each other, to have a close platonic bond, to be the best of friends
            \begin{quote}
                nemi i\textsc{b}aa\textsc{t}ami\\
                \textit{`The two of us are thick as thieves.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{BiBiyaT}{v.tr.}\label{word:BiBiyaT}
        \dictdef*{
            to point \textit{smth.} out, to make \textit{smth.} known, to tell \textit{smth.}, to make \textit{smth.} obvious, to show \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaBiT}{v.tr.}\label{word:aaBiT}
        \dictdef*{
            to tell \textit{sme.}, to let \textit{sme.} know
            \begin{quote}
                \famword{TaT mi BiiTuc udan (bus fun) nas aaBiTibiak.}\\
                \textit{`If you know the news, tell me (it).'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{BaTa}{adj.}\label{word:BaTa}
        \dictdef*{
            knowledgeable, understanding, wise
        }
    \end{dictentry}
    \begin{dictentry}{uBiTi}{adj.}\label{word:uBiTi}
        \dictdef*{
            smug, arrogant, full of oneself, feeling like one knows everything
        }
    \end{dictentry}
    \begin{dictentry}{BanaT}{n.}\label{word:BanaT}
        \dictdef{
            expert, source, knowledgeable person
        }
        \dictdef{
            chief, head, boss
        }
    \end{dictentry}
    \begin{dictentry}{BuliT}{n.}\label{word:BuliT}
        \dictdef*{
            head
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{BaTaisa}{n.}\label{word:BaTaisa}
        \dictdef*{
            knowledgeableness, wisdom
        }
    \end{dictentry}
    \begin{dictentry}{uBiTiisa}{n.}\label{word:uBiTiisa}
        \dictdef*{
            smugness, arrogance
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{br}{t}\label{root:BR_T}
    % Wales, Welsh, Great Britain
    \begin{dictentry}{BRuuT}{n.}\label{word:BRuuT}
        \dictdef{
            Wales
        }
        \dictdef{
            the Welsh people
        }
        \dictdef{
            Great Britain
        }
        \dictdef{
            the British people
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{bw}{\bigglot}\label{root:BW_7}
    \begin{dictentry}{BWa\bigglot}{n.}\label{word:BWa7}
        \dictdef*{
            month (of the year)
        }
    \end{dictentry}
    \begin{dictentry}{BWiya\bigglot}{v.intr.}\label{word:BWiya7}
        \dictdef*{
            to recur on a monthly basis, to be monthly
        }
    \end{dictentry}
    \begin{dictentry}{iBWaa\bigglot}{v.intr.}\label{word:iBWaa7}
        \dictdef*{
            to be on one's period, to be menstruating
        }
    \end{dictentry}
    \begin{dictentry}{BWa\bigglot a}{adj.}\label{word:BWa7a}
        \dictdef{
            monthly, per month
        }
        \dictdef{
            menstrual
        }
    \end{dictentry}
    \begin{dictentry}{uBWi7i}{adj.}
        \dictdef{
            moody, crampy, bloated, feeling the symptoms of PMS or period cramps
        }
    \end{dictentry}
    \begin{dictentry}{iBWu\bigglot a}{n.}\label{word:iBWu7a}
        \dictdef*{
            period, menstruation, `that time of the month'
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{awkus-BWa\bigglot}{n.}\label{word:awkus-BWa7}
        \dictdef*{
            August, 8th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{disi-BWa\bigglot}{n.}\label{word:disi-BWa7}
        \dictdef*{
            December, 12th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{ephii-BWa\bigglot}{n.}\label{word:ephii-BWa7}
        \dictdef*{
            April, 4th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{fi-BWa\bigglot}{n.}\label{word:fi-BWa7}
        \dictdef*{
            February, 2nd month of the Gregorian calendar
            }
    \end{dictentry}
    \begin{dictentry}{jan-BWa\bigglot}{n.}\label{word:jan-BWa7}
        \dictdef*{
            January, 1st month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{juu\lilglot li-BWa\bigglot}{n.}\label{word:juu7li-BWa7}
        \dictdef*{
            July, 7th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{juu\lilglot ni-BWa\bigglot}{n.}\label{word:juu7ni-BWa7}
        \dictdef*{
            June, 6th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{maats-BWa\bigglot}{n.}\label{word:maats-BWa7}
        \dictdef*{
            March, 3rd month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{maj-BWa\bigglot}{n.}\label{word:maj-BWa7}
        \dictdef*{
            May, 5th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{nufim-BWa\bigglot}{n.}\label{word:nufim-BWa7}
        \dictdef*{
            November, 11th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{sepcim-BWa\bigglot}{n.}\label{word:sepcim-BWa7}
        \dictdef*{
            September, 9th month of the Gregorian calendar
        }
    \end{dictentry}
    \begin{dictentry}{uktuu-BWa\bigglot}{n.}\label{uktuu-BWa7}
        \dictdef*{
            October, 10th month of the Gregorian calendar
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    C
%%%%%%%%%%%
\section*{C}

\begin{dictroot}{c}{c}\label{root:C_C}
    % example
    \begin{dictentry}{CaC}{n.}\label{word:CaC}
        \dictdef{
            example
        }
        \dictdef{
            such an idea, an idea like that
        }
    \end{dictentry}
    \begin{dictentry}{CiiC}{v.tr}\label{word:CiiC}
        \dictdef*{
            to serve as an example of \textit{smth.}
            \begin{quote}
                \famword{[SMTH] [ELSE] CiiC.}\\
                \textit{[SMTH] is an example of [ELSE].}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{CiyaC}{v.intr.}\label{word:CiyaC}
        \dictdef*{
            to be an example, to serve as an example
            \begin{quote}
                \famword{[SENT]. [THING] CiyaC.}\\
                \textit{[SENT]. For example, [THING].}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{iCaaC}{v.intr.}\label{word:iCaaC}
        \dictdef*{
            to give an example, to provide an example
            \begin{quote}
                \famword{nas iCaaCuc mi kajli?}\\
                \textit{Do you want me to give an example?}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{CiCiyaC}{v.tr.}\label{word:CiCiyaC}
        \dictdef*{
            to use \textit{smth. or sme.} as an example, to make an example of \textit{smth. or sme.}
            \begin{quote}
                \famword{mi iBaaJe\lilglot{} hakuc udan aaSKiLana mi qaa[PUNISH]ibi7 CiCiyaCibi.}\\
                \textit{If you keep misbehaving, the teacher will punish you to make an example out of you.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{aaCiC}{v.tr.}\label{word:aaCiC}
        \dictdef*{
            to ask \textit{sme.} for an example, to make \textit{sme.} give an example
            \begin{quote}
                \famword{pars aaSKiLana aaCiCibi.}\\
                \textit{The teacher asked him for an example.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{CurCi}{n.}\label{word:CurCi}
        \dictdef*{
            prototype, example of a physical product
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{f}\label{root:C_F}
    \begin{dictentry}{CaF}{n.}\label{word:CaF}
        \dictdef{
            number
        }
        \dictdef{
            amount
        }
    \end{dictentry}
    \begin{dictentry}{CiiF}{v.tr.}\label{word:CiiF}
        \dictdef*{
            to number \textit{some amount}, to measure out to \textit{some amount}
            \begin{quote}
                \famword{naswi bar CiiF.}\\
                \textit{There are three of us. (lit., `We number three.')}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{CiyaF}{v.intr.}\label{word:CiyaF}
        \dictdef*{
            to be counted, to be measured, to have one's quantity kept track of
            \begin{quote}
                \famword{[OXYGEN LEVEL] [CAREFUL]e\lilglot{} CiyaFe\lilglot{} tuuq}\\
                \textit{Oxygen levels must be carefully kept track of.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{iCaaF}{v.intr.}\label{word:iCaaF}
        \dictdef*{
            to count things, to measure things
            \begin{quote}
                \famword{nas iCaaFe\lilglot{} dak!}\\
                \textit{I can count!}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{CiCiyaF}{v.tr.}\label{word:CiCiyaF}
        \dictdef*{
            to count \textit{smth.}, to measure \textit{smth.}, to keep track of \textit{smth.}'s quantity
            \begin{quote}
                \famword{nas [BLOOD SUGAR] CiCiyaFe\lilglot{} tuuq.}\\
                \textit{I need to measure my blood sugar.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{aaCiF}{v.tr.}\label{word:aaCiF}
        \dictdef*{
            to count out \textit{smth.}, to measure out \textit{smth.}, to set aside a quantity of \textit{smth.}
            \begin{quote}
                \famword{sesardam inPiDinilat KarLi aaCiCak.}\\
                \textit{Measure out three-hundred milliliters of water.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{CimiFu}{n.}\label{word:CimiFu}
        \dictdef*{
            measuring cup, a container for measuring the quantity of something by volume
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{j}\label{root:C_J}
    %speed, fast, rush, urgent, horse
    \begin{dictentry}{CaJ}{n.}\label{word:CaJ}
        \dictdef*{
            speed
        }
    \end{dictentry}
    \begin{dictentry}{CiiY}{v.tr.}\label{word:CiiY}
        \dictdef*{
            to hurry over \textit{smth.}, to rush \textit{smth.}, to do \textit{smth.} in a hurry
        }
    \end{dictentry}
    \begin{dictentry}{CiyaJ}{v.intr.}\label{word:CiyaJ}
        \dictdef*{
            to be hurried, to be rushed, to be expedited
        }
    \end{dictentry}
    \begin{dictentry}{iCaaJ}{v.intr.}\label{word:iCaaJ}
        \dictdef*{
            to hurry, to rush, to make haste, to be quick about things
        }
    \end{dictentry}
    \begin{dictentry}{CiCiyaJ}{v.tr.}\label{word:CiCiyaJ}
        \dictdef*{
            to hasten \textit{smth.}, to cause \textit{smth.} to be rushed, to expedite, to cut corners on \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaCiY}{v.tr.}\label{word:aaCiY}
        \dictdef*{
            to be urgent to \textit{sme.}, to merit \textit{sme.}'s haste, cause \textit{sme.} to hurry over
            \begin{quote}
                \famword{[CLIMATE CHANGE] RaTa [WORLD] aaCiJibi}\\
                \textit{`Climate change is urgent for the entire world.'}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{CuJu}{n.}\label{word:CuJu}
        \dictdef*{
            horse
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{mp}\label{root:C_MP}
    %jump, kangaroo
    \begin{dictentry}{CiyaMP}{v.intr.}\label{word:CiyaMP}
        \dictdef*{
            to bounce
        }
    \end{dictentry}
    \begin{dictentry}{iCaaMP}{v.intr.}\label{word:iCaaMP}
        \dictdef*{
            to jump
        }
    \end{dictentry}
    \begin{dictentry}{CuMPu}{n.}\label{word:CuMPu}
        \dictdef*{
            kangaroo, wallaby
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{n}\label{root:C_N}
    %to climb, to crawl, to scramble
    \begin{dictentry}{CiiN}{v.tr.}\label{word:CiiN}
        \dictdef*{
            to scale \textit{smth.}, climb up \textit{smth.}, to crawl along or through \textit{smth.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{nk}\label{root:C_NK}
    \begin{dictentry}{CaNK}{n.}\label{word:CaNK}
        \dictdef*{
            roundness
        }
    \end{dictentry}
    \begin{dictentry}{CiiNK}{v.tr.}\label{word:CiiNK}
%we need more thought about this one here
        \dictdef*{
            to roll \textit{smth.} along
        }
    \end{dictentry}
%shouldn't these be CiyaNK and CiCiyaNK?
    \begin{dictentry}{CiyaNK}{v.intr.}\label{word:CiyaNK}
        \dictdef*{
            to roll, to tumble, to be rolled along
        }
    \end{dictentry}
    \begin{dictentry}{iCaaNK}{v.intr.}\label{word:iCaaNK}
        \dictdef{
            to tumble, to roll oneself along, to roll around
        }
    \end{dictentry}
    \begin{dictentry}{CaNKa}{adj.}\label{word:CaNKa}
        \dictdef{
            round
        }
        \dictdef{
            fat
        }
        \dictdef{
            full
        }
    \end{dictentry}
    \begin{dictentry}{uCiNKi}{adj.}\label{word:uCiNKi}
        \dictdef{
            feeling full, feeling fat, bloated
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{r}\label{root:C_R}
    \begin{dictentry}{CanaR}{n.}\label{word:CanaR}
        \dictdef*{servant, maid, hired help, `the help'\\\textit{NB: derived from Danish \emph{tjener}, considered somewhat patronizing}}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{c}{w}\label{root:C_W}
    \begin{dictentry}{CiiW}{v.tr.}\label{word:CiiW}
        \dictdef*{
            to remember fondly, reminisce, be nostalgic about \emph{smth.} or \emph{sme.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{cl}{d}\label{root:CL_D}
    % to wear
    \begin{dictentry}{CLaD}{n.}\label{word:CLaD}
        \dictdef{
            clothing
        }
    \end{dictentry}
    \begin{dictentry}{CLiiD}{v.tr.}\label{word:CLiiD}
        \dictdef*{
            to wear \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{CLiyaD}{v.intr.}\label{word:CLiyaD}
        \dictdef*{
            \textit{(of clothing)} to be worn, to be put on
        }
    \end{dictentry}
    \begin{dictentry}{iCLaaD}{v.intr.}\label{word:iCLaaD}
        \dictdef*{
            to get dressed, to put clothes on
        }
    \end{dictentry}
    \begin{dictentry}{CLiCLiyaD}{v.tr.}\label{word:CLiCLiyaD}
        \dictdef*{
            \textit{(of a piece of clothing)} to put \textit{smth.} on, to get dressed in \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaCLiD}{v.tr.}\label{word:aaCLiD}
        \dictdef*{
            to dress \textit{sme.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{cm}{s}\label{root:CM_S}
    \begin{dictentry}{CMiiS}{v.tr}\label{word:CMiiS}
        \dictdef*{
            to cut, to slice
        }
    \end{dictentry}
    \begin{dictentry}{meCMiiS}{n.}\label{word:mCMiiS}
        \dictdef*{
            knife
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    D
%%%%%%%%%%%
\section*{D}

\begin{dictroot}{d}{l}\label{root:D_L}
    \begin{dictentry}{DaL}{n.}\label{word:DaL}
        \dictdef*{
            sight
        }
    \end{dictentry}  
    \begin{dictentry}{DiiL}{v.tr.}\label{word:DiiL}
        \dictdef{
            to stare intently at
        }
        \dictdef{
            to inspect, supervise
        }
    \end{dictentry}
    \begin{dictentry}{DiyaL}{v.intr.}\label{word:DiyaL}
        \dictdef*{
            to appear, seem, be perceived
        }
    \end{dictentry}
    \begin{dictentry}{iDaaL}{v.intr.}\label{word:iDaaL}
        \dictdef{
            to look, watch, stare
        }
        \dictdef{
            to supervise, watch over
        }
    \end{dictentry}
    \begin{dictentry}{DiDiyaL}{v.tr.}\label{word:DiDiyaL}
        \dictdef{
            to show, to display
        }
        \dictdef{
            to publish
        }
        \dictdef{
            to broadcast
        }
    \end{dictentry}
    \begin{dictentry}{aaDiL}{v.tr.}\label{word:aaDiL}
        \dictdef*{
            to draw \textit{sme.'s} attention, to make a scene
        }
    \end{dictentry}
    \begin{dictentry}{DaLa}{adj.}\label{word:DaLa}
        \dictdef*{
            visible
        }
    \end{dictentry}
    \begin{dictentry}{DanaL}{n.}\label{word:DanaL}
        \dictdef{
            audience, spectator, onlooker
        }
        \dictdef{
            supervisor
        }
    \end{dictentry}
    \begin{dictentry}{DurLi}{n.}\label{word:DurLi}
        \dictdef{
            eyeball
        }
        \dictdef{
            \textit{(fig.)} the apple of one's eye
        }
    \end{dictentry}
    \begin{dictentry}{DarLi}{n.}\label{word:DarLi}
        \dictdef*{
            tear, tears
        }
    \end{dictentry}
    \begin{dictentry}{iDuLa}{n.}\label{word:iDuLa}
        \dictdef{
            theater, movie theater
        }
        \dictdef{
            arena
        }
        \dictdef{
            stage
        }
    \end{dictentry}
    \begin{dictentry}{mDiL}{n.}\label{word:mDiL}
        \dictdef{
            lens
        }
        \dictdef{
            glasses
        }
    \end{dictentry}
    \begin{dictentry}{inDiL}{n.}\label{word:inDiL}
        \dictdef*{
            glance, brief look
        }
    \end{dictentry}
    \begin{dictentry}{DuliL}{n.}\label{word:DuliL}
        \dictdef*{
            eye, complex eye, compound eye, photosensitive tissue
        }
    \end{dictentry}
    %\begin{dictentry}{DuLu}{n.}
    %    \dictdef*{

    %    }
    %\end{dictentry}
    %\begin{dictentry}{DasiL}{n.}
    %    \dictdef*{

    %    }
    %\end{dictentry}
    %\begin{dictentry}{DajuLa}{n.}
    %    \dictdef*{
    %        mirror
    %    }
    %\end{dictentry}
    %\begin{dictentry}{DidiL}{n.}
    %    \dictdef*{

    %    }
    %\end{dictentry}
    \begin{dictentry}{aDiLu}{n.}\label{word:aDiLu}
        \dictdef{
            scene, performance
        }
        \dictdef{
            television program
        }
    \end{dictentry}
    %\begin{dictentry}{DimiLu}{n.}
    %    \dictdef*{

    %    }
    %\end{dictentry}
    %\begin{dictentry}{DuLi}{n., adj.}
    %    \dictdef*{

    %    }
    %\end{dictentry}
    %\begin{dictentry}{uDiLi}{adj.}
    %    \dictdef*{

    %    }
    %\end{dictentry}

\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{HWaDa-mDiL}{n.}\label{word:HwaDa-mDiL}
        \dictdef{
            microscope
        }
    \end{dictentry}
    \begin{dictentry}{NaSamDiL}{n.}\label{word:NaSamDiL}
        \dictdef{
            optical (i.e. not outside visible spectrum) telescope, binoculars
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{d}{m}\label{root:D_M}
    % to meet, to come across
    % also to gather, to meet up
    \begin{dictentry}{DaM}{n.}\label{word:DaM}
        \dictdef{
            meeting, meet-up, gathering, rendezvous, date
        }
        \dictdef{
            introduction, meeting, first encounter
        }
        \dictdef{
            encounter, brush, confrontation
        }
    \end{dictentry}
    \begin{dictentry}{DiiM}{v.tr.}\label{word:DiiM}
        \dictdef*{
            to meet \textit{sme.}, to come across \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{DiyaM}{v.intr.}\label{word:DiyaM}
        \dictdef*{
            to be met, to be encountered, to be found, to be come across
        }
    \end{dictentry}
    \begin{dictentry}{iDaaM}{v.intr.}\label{word:iDaaM}
        \dictdef*{
            to meet up, to gather, to go somewhere for the purpose of meeting someone
        }
    \end{dictentry}
    \begin{dictentry}{DiDiyaM}{v.tr.}\label{word:DiDiyaM}
        \dictdef*{
            to introduce \textit{smth. or sme.}, to present \textit{smth. or sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaDiM}{v.tr.}\label{word:aaDiM}
        \dictdef*{
            to bring \textit{smth. or sme.} together, to rangle \textit{smth.} up, to herd together
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{LaF-DaM}{n.}
        \dictdef*{
            romantic rendezvous, romantic date, meet-up for romantic purposes\\
            \textit{NB: more often just shortened to \famword{LaF} or \famword{DaM} in casual speech}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{d}{n}\label{root:D_N}
    \begin{dictentry}{DanaN}{n.}\label{word:DanaN}
        \dictdef{
            Dane, Danish person
        }
        \dictdef{
            \textit{(slang)} cop, police
        }
    \end{dictentry}
    \begin{dictentry}{DuuN}{n.}\label{word:DuuN}
        \dictdef{
            Denmark
        }
        \dictdef{
            ethnically Danish people
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{dr}{j}\label{root:DR_J}
    \begin{dictentry}{DRaJ}{n.}\label{word:DRaJ}
        \dictdef*{
            magic, witchcraft
        }
        \dictdef*{
            a magic spell, a magical curse
        }
    \end{dictentry}
    \begin{dictentry}{DRiiY}{v.tr}\label{word:DRiiY}
        \dictdef*{
            to cast a spell on \textit{smth. or sme.}
        }
    \end{dictentry}
    \begin{dictentry}{DRanaJ}{n.}\label{word:DRanaJ}
        \dictdef*{
            witch, druid, sorcerer, wizard
        }
    \end{dictentry}
    \begin{dictentry}{DRuuJ}{n.}\label{word:DRuuJ}
        \dictdef{
            pagan people group(s), pagan people(s)
        }
        \dictdef{
            pagan, practicer of pagan religious practices
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{dr}{p}\label{root:DR_P}
    \begin{dictentry}{DRaP}{n.}\label{word:DRaP}
        \dictdef{%
        bad accent, mispronunciation
        }
        \dictdef{%
        funny voice, impression
            \begin{quote}
                \famword{buse wan DRaP lit.} \\
                \textit{`Their impression was really bad.'}
            \end{quote}
        }
        \dictdef{
            flub, speech error
        }
        \dictdef{
            misquote
        }
    \end{dictentry}
    \begin{dictentry}{DRiiP}{v.tr.}\label{word:DRiiP}
        \dictdef*{%
        to mimic \textit{sme.}, make fun of \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{DRiyaP}{v.intr.}\label{word:DRiyaP}
        \dictdef{
            to sound funny, to be mispronounced or said in a weird way
        }
        \dictdef{
            \textit{(fig.)} to be awkwardly worded, to be poorly put-together as a statement, to be a flub or speech error
        }
    \end{dictentry}
    \begin{dictentry}{iDRaaP}{v.intr.}\label{word:iDRaaP}
        \dictdef*{%
            to talk with an accent, talk in a funny voice
        }
    \end{dictentry}
    \begin{dictentry}{DRiDRiyaP}{v.tr.}\label{word:DRiDRiyaP}
        \dictdef{
            to mispronounce \textit{smth.}, to say \textit{smth.} in a funny way
        }
        \dictdef{
            \textit{(fig.)} to flub saying \textit{smth.}, to say \textit{smth.} poorly
        }
    \end{dictentry}
    \begin{dictentry}{aaDRiP}{v.tr.}\label{word:aaDRiP}
        \dictdef*{
            to misquote \textit{sme.}, to misrepresent what \textit{sme.} says
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    F
%%%%%%%%%%%
\section*{F}

\begin{dictroot}{f}{f}\label{root:F_F}
    \begin{dictentry}{FaF}{n.}\label{word:FaF}
        \dictdef*{scent, smell, fragrance}
    \end{dictentry}
    \begin{dictentry}{FiyaF}{v.intr.}\label{word:FiyaF}
        \dictdef*{to smell, to emit scent, to be fragrant}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{f}{l}\label{root:F_L}
    \begin{dictentry}{FaL}{n.}\label{word:FaL}
        \dictdef*{
            impression
        }
    \end{dictentry}
    \begin{dictentry}{FiiL}{v.tr.}\label{word:FiiL}
        \dictdef*{
            to notice \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{FiyaL}{v.intr.}\label{word:FiyaL}
        \dictdef*{
            to be distracted, have one's attention be diverted from something
        }
    \end{dictentry}
    \begin{dictentry}{iFaaL}{v.intr.}\label{word:iFaaL}
        \dictdef*{
            to be on the lookout, stay alert so as to catch an unplanned and spontaneous sensory impression
            \begin{quote}
                \famword{HWanaD wan BuRKu daw naswi iFaaL.} \\
                \textit{`We kept an eye out for the neighbor's dog.'}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{FiFiyaL}{v.tr.}\label{word:FiFiyaL}
        \dictdef*{
            to distract \textit{sme.}, draw \textit{sme.'s} attention away from their current focus
        }
    \end{dictentry}
    \begin{dictentry}{aaFiL}{v.tr.}\label{word:aaFiL}
        \dictdef*{
            to divert \textit{sme.'s} attention towards something else, especially an incoming impression
            \begin{quote}
                \famword{bu MaNTa QasiH daw nas liWSaN dis aaFiLe{\lilglot} hwiili?} \\
                \textit{`Why didn't you warn me about that huge snake?'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{FanaL}{n.}\label{word:FanaL}
        \dictdef{
            watch, watchman
        }
        \dictdef{
            policeman, trooper
        }
    \end{dictentry}
    \begin{dictentry}{FuLaw}{n., adv.}\label{word:FuLaw}
        \dictdef{
            the left hand
        }
        \dictdef{
            to the left, on the left side
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{f}{m}\label{root:F_M}
    \begin{dictentry}{FaM}{n.}\label{word:FaM}
        \dictdef*{
            language, speech, way of speaking
        }
    \end{dictentry}
    \begin{dictentry}{FiiM}{v.tr.}\label{word:FiiM}
        \dictdef*{
            to say \textit{smth.}, to speak \textit{smth.}, to tell \textit{smth.}, to talk about \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{FiyaM}{v.intr.}\label{word:FiyaM}
        \dictdef*{
            to be said, to be distributed, to be published, to be broadcast
        }
    \end{dictentry}
    \begin{dictentry}{iFaaM}{v.intr.}\label{word:iFaaM}
        \dictdef*{
            to talk, to speak, to chatter
        }
    \end{dictentry}
    \begin{dictentry}{FiFiyaM}{v.tr.}\label{word:FiFiyaM}
        \dictdef*{
            to publish, to distribute, to broadcast
        }
    \end{dictentry}
    \begin{dictentry}{aaFiM}{v.tr.}\label{word:aaFiM}
        \dictdef*{
            to quote \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{iFuMa}{n.}\label{word:iFuMa}
        \dictdef{
            conversation
        }
        \dictdef{
            \textit{(internet)} server, board, forum
        }
    \end{dictentry}
    \begin{dictentry}{inFiM}{n.}\label{word:inFiM}
        \dictdef*{
            word
        }
    \end{dictentry}
    \begin{dictentry}{FuMi}{adj.}\label{word:FuMi}
        \dictdef*{
            wordy, dense, difficult to understand due to too many or too complicated words
        }
    \end{dictentry}
    \begin{dictentry}{FuliM}{n.}\label{word:FuliM}
        \dictdef{
            mouth
        }
        \dictdef{
            tongue
        }
    \end{dictentry}
    \begin{dictentry}{FuMu}{n.}\label{word:FuMu}
        \dictdef*{
            human, \textit{Homo sapiens sapiens}
        }
    \end{dictentry}
    \begin{dictentry}{FasiM}{n.}\label{word:FasiM}
        \dictdef*{
            thread (of a conversation, of a forum)
        }
    \end{dictentry}
    \begin{dictentry}{aFiMu}{n.}\label{word:aFiMu}
        \dictdef{
            book
        }
    \end{dictentry}
    \begin{dictentry}{FimiMu}{n.}\label{word:FimiMu}
        \dictdef{
            \textit{(of a radio or television network)} channel, station, frequency
        }
        \dictdef{
            \textit{(internet)} channel, chatroom
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{inFiMini}{n.}\label{word:inFiMini}
        \dictdef*{
            letter, character, symbol
        }
    \end{dictentry}
    \begin{dictentry}{{\bigglot}a{\bigglot}a-FaM}{n.}\label{word:7a7a-FaM}
        \dictdef*{
            this language, \lang{}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{f}{s}\label{root:F_S}
    \begin{dictentry}{FaS}{n.}\label{word:FaS}
        \dictdef{
            life, life force
        }
        \dictdef{
            birth
        }
    \end{dictentry}
    \begin{dictentry}{FiiS}{v.tr.}\label{word:FiiS}
        \dictdef{
            \textit{(of a human)} to give birth to \textit{sme.}
        }
        \dictdef{
            \textit{(of an animal that bears live young)} to give birth to its offspring
        }
        \dictdef{
            \textit{(of an animal that lays eggs)} to hatch its offspring
        }
    \end{dictentry}
    \begin{dictentry}{FiyaS}{v.intr.}\label{word:FiyaS}
        \dictdef*{
            to live, to be alive
        }
    \end{dictentry}
    \begin{dictentry}{iFaaS}{v.intr.}\label{word:iFaaS}
        \dictdef{
            to wake up, to awaken
        }
        \dictdef{
            to liven up, to become lively and energetic, to pep up
        }
    \end{dictentry}
    \begin{dictentry}{FiFiyaS}{v.tr.}\label{word:FiFiyaS}
        \dictdef*{
            to resuscitate \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaFiS}{v.tr.}\label{word:aaFiS}
        \dictdef{
            to wake \textit{sme.} up
        }
        \dictdef{
            to animate \textit{smth.}, bring life to \textit{smth}
        }
    \end{dictentry}
    \begin{dictentry}{FaSa}{adj.}\label{word:FaSa}
        \dictdef{
            alive
        }
        \dictdef{
            awake
        }
    \end{dictentry}
    \begin{dictentry}{uFiSi}{adj.}\label{word:uFiSi}
        \dictdef*{
            lively, spry
        }
    \end{dictentry}
    \begin{dictentry}{FanaS}{n.}\label{word:FanaS}
        \dictdef*{
            person, predominantly human or humanoid
        }
    \end{dictentry}
    \begin{dictentry}{FurSi}{n.}\label{word:FurSi}
        \dictdef*{
            egg
        }
    \end{dictentry}
    \begin{dictentry}{FarSi}{n.}\label{word:FarSi}
        \dictdef*{
            blood
        }
    \end{dictentry}
    \begin{dictentry}{iFuSa}{n.}\label{word:iFuSa}
        \dictdef{
            house
        }
        \dictdef{
            home, domicile
        }
    \end{dictentry}
    \begin{dictentry}{inFiS}{n.}\label{word:inFiS}
        \dictdef*{
            human offspring, especially newborn-through-toddler age
        }
    \end{dictentry}
    \begin{dictentry}{FuliS}{n.}\label{word:FuliS}
        \dictdef*{
            heart
        }
    \end{dictentry}
    \begin{dictentry}{FuSu}{n.}\label{word:FuSu}
        \dictdef*{
            animal, any species of the kingdom Animalia except humans
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{JanaS-FaS}{n.}
        \dictdef*{Christmas, the birth of Christ}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{fr}{nc}\label{root:FR_NC}
    % France
    \begin{dictentry}{FRuuNC}{n.}\label{word:FRuuNC}
        \dictdef*{
            the Franks
        }
    \end{dictentry}
    \begin{dictentry}{FRaNCia}{n.}\label{word:FRaNCia}
        \dictdef*{
            France
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    H
%%%%%%%%%%%
\section*{H}

\begin{dictroot}{h}{h}\label{root:H_H}
    % to smoke
    \begin{dictentry}{HiiH}{v.tr.}\label{word:HiiH}
        \dictdef*{
            to smoke \textit{smth.}, to inhale smoke from burning \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{HiyaH}{v.intr.}\label{word:HiyaH}
        \dictdef{
            to be smoked, to be bathed in smoke, to be preserved by smoke
        }
        \dictdef{
            \textit{(fig.)} to inhale secondhand smoke
        }
    \end{dictentry}
    \begin{dictentry}{iHaaH}{v.intr.}\label{word:iHaaH}
        \dictdef{
            to smoke a tobacco or marijuana product, to be smoking, to deliberately inhale smoke
        }
        \dictdef{
            to emit smoke, to create smoke, to have smoke coming off of oneself
        }
    \end{dictentry}
    \begin{dictentry}{HiHiyaH}{v.tr.}\label{word:HiHiyaH}
        \dictdef{
            to smoke \textit{smth.}, to immerse in smoke, to cure by smoking
        }
        \dictdef{
            \textit{(fig.)} to smoke too near \textit{sme.}, to force \textit{sme.} to breathe in one's secondhand smoke
        }
    \end{dictentry}
    \begin{dictentry}{HaHa}{adj.}\label{word:HaHa}
        \dictdef*{
            smoky
        }
    \end{dictentry}
    \begin{dictentry}{HarHi}{n.}\label{word:HarHi}
        \dictdef*{
            smoke
        }
    \end{dictentry}
    \begin{dictentry}{HasiH}{n.}\label{word:HasiH}
        \dictdef*{
            plume of smoke
        }
    \end{dictentry}
    \begin{dictentry}{uHiHi}{adj.}\label{word:uHiHi}
        \dictdef*{
            confused, disoriented
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{h}{j}\label{root:H_J}
    \begin{dictentry}{HaJ}{n.}\label{word:HaJ}
        \dictdef*{
            light, brightness, illumination, luminosity
        }
    \end{dictentry}
    \begin{dictentry}{HiiY}{v.tr.}\label{word:HiiY}
        \dictdef{
            to illuminate, to brighten, to fill with light
        }
        \dictdef{
            \textit{(of a dwelling)} to move in \textit{smwh.}, to set up residence
        }
        \dictdef{
            \textit{(of a place of business)} to open \textit{smth.}, to begin business
        }
    \end{dictentry}
    \begin{dictentry}{HiyaJ}{v.intr.}\label{word:HiyaJ}
        \dictdef{
            to shine, to glow, to give out light
        }
        \dictdef{
            \textit{(impersonal)} to be bright out, to be sunny, to sun-shine, to be daylight, to be light out
            \begin{quote}
                \famword{HiyaJ, nemi iLaaSak!}\\
                \textit{The sun's shining, let's take a walk!}
            \end{quote}
        }
        \dictdef{
            \textit{(of a dwelling)} to have the lights on, to be currently filled with people going about their business
            \begin{quote}
                \famword{bu aFiSu HiyaJ FanaS irfituru.}\\
                \textit{That house has the lights on, someone must be inside.}
            \end{quote}
        }
        \dictdef{
            \textit{(of a place of business)} to be open, to be in operation, to be accepting customers
            \begin{quote}
                M\famword{AMA}-I\famword{NUMA se FS\,1 fun SJ\,3 daw iHaaJ}\\
                \textit{Mama-Inuma is open from 7\textsc{am} to 9\textsc{pm}.}
            \end{quote}
        }
        \dictdef{
            \textit{(of a device)} to be on, to be working
        }
    \end{dictentry}
    \begin{dictentry}{iHaaJ}{v.intr.}\label{word:iHaaJ}
        \dictdef{
            to turn on, to begin emitting light
        }
        \dictdef{
            \textit{(impersonal, of the sun)} to come out, to begin shining
        }
        \dictdef{
            to open, to begin business, to begin serving customers either for the day or in general
        }
        \dictdef{
            \textit{(of a device)} to turn on, to begin working
        }
    \end{dictentry}
    \begin{dictentry}{HiHiyaJ}{v.tr.}\label{word:HiHiyaJ}
        \dictdef{
            to cause to shed light, to light \textit{(a torch)}, to turn on \textit{(a lamp)}
            \begin{quote}
                \famword{wa PLaS fit HaTauru, mHiY HiHiyaJak.}\\
                \textit{It's dark in here, turn on the light.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{aaHiY}{v.tr.}\label{word:aaHiY}
        \dictdef{
            \textit{(of a device)} to turn \textit{smth.} on, to power \textit{smth.} up
            \begin{quote}
                \famword{nas mFiM aaHiYe\lilglot{} tuuq.}\\
                \textit{I need to turn on my phone.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{HaJa}{adj.}\label{word:HaJa}
        \dictdef{
            bright, light, glowing, alight
        }
        \dictdef{\textit{
            (of a place of business)} open, in operation, accepting customers
        }
        \dictdef{
            \textit{(of a device)} powered on, in operation, working
        }
    \end{dictentry}
    \begin{dictentry}{uHiYi}{adj.}\label{word:uHiYi}
        \dictdef*{
            dazzled, impressed, overwhelmed
        }
    \end{dictentry}
    \begin{dictentry}{HanaJ}{n.}\label{word:HanaJ}
        \dictdef*{
            the Sun
        }
    \end{dictentry}
    \begin{dictentry}{HurYi}{n.}\label{word:HurYi}
        \dictdef*{
            orb of light, as from around a torch, lantern, or other non-diffuse light source
        }
    \end{dictentry}
    \begin{dictentry}{HarYi}{n.}\label{word:HarYi}
        \dictdef{
            Aurora Borealis, the Northern Lights
        }
        \dictdef{
            \textit{(physics)} plasma, the state of matter consisting of partially ionized gas
        }
    \end{dictentry}
    \begin{dictentry}{iHuJa}{n.}\label{word:iHuJa}
        \dictdef*{
            day, daytime
        }
    \end{dictentry}
    \begin{dictentry}{mHiY}{n.}\label{word:mHiY}
        \dictdef{
            lamp, light \textit{(apparatus)}
        }
        \dictdef{
            projector
        }
    \end{dictentry}
    \begin{dictentry}{inHiY}{n.}\label{word:inHiY}
        \dictdef*{
            twinkle, sparkle
        }
    \end{dictentry}
    \begin{dictentry}{HuliY}{n.}\label{word:HuliY}
        \dictdef*{
            retina
        }
    \end{dictentry}
    \begin{dictentry}{HuJu}{n.}\label{word:HuJu}
        \dictdef*{
            firefly, lightning bug, glowworms, bioluminescent insect
        }
    \end{dictentry}
    \begin{dictentry}{HasiY}{n.}\label{word:HasiY}
        \dictdef{
            beam of light, sunbeam, ray of light
        }
        \dictdef{
            laser
        }
    \end{dictentry}
    \begin{dictentry}{HajuJa}{n.}\label{word:HajuJa}
        \dictdef{
            a field of light projected onto any unlit surface
            \begin{quote}
                \famword{CuSu HajuJa fit iYaaN.}\\
                \textit{The cat lay down to bask in the light.}
            \end{quote}
            }
        \dictdef{
            an image or moving images projected onto a screen, as in a cinema or office presentation
            \begin{quote}
                \famword{inFiM par HajuJa tui BaCauru\lilglot lit.}\\
                \textit{The words in that slide are very small.}
            \end{quote}
            }
        \dictdef{
            any backlit screen, as in a television or monitor
            \begin{quote}
                \famword{mFiM wan HajuJa daw fit nas iLaaS, was iHaaJe\lilglot{} kaje\lilglot{} hwii\lilglot{} wadan.}\\
                \textit{I stepped on my phone's screen, and now it won't turn on.}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{HidiY}{n.}\label{word:HidiY}
        \dictdef*{
            photon
        }
    \end{dictentry}
    \begin{dictentry}{aHiYu}{n.}\label{word:aHiYu}
        \dictdef*{
            lantern, lightbulb
        }
    \end{dictentry}
    \begin{dictentry}{HimiYu}{n.}\label{word:HimiYu}
        \dictdef*{
            candle, torch
        }
    \end{dictentry}
    \begin{dictentry}{HuJaw}{n., adv.}\label{word:HuJaw}
        \dictdef{
            south
        }
        \dictdef{
            southwards, to the south, in the south
        }
        \dictdef{
            clockwise
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{dajHuJa}{n.}\label{word:dajHuJa}
        \dictdef*{
            tomorrow
        }
    \end{dictentry}
    \begin{dictentry}{fajHuJa}{n.}\label{word:fajHuJa}
        \dictdef*{
            yesterday
        }
    \end{dictentry}
    \begin{dictentry}{wajHuJa}{n.}\label{word:wajHuJa}
        \dictdef*{
            today
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{h}{nk}\label{root:H_NK}
    % goose, honk, annoy
    \begin{dictentry}{HiiNK}{v.tr.}\label{word:HiiNK}
        \dictdef*{
            to annoy \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{iHaaNK}{v.intr.}\label{word:iHaaNK}
        \dictdef*{
            to honk
        }
    \end{dictentry}
    \begin{dictentry}{HaNKa}{adj.}\label{word:HaNKa}
        \dictdef*{
            annoying
        }
    \end{dictentry}
    \begin{dictentry}{HuNKu}{n.}\label{word:HuNKu}
        \dictdef*{
            goose
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{h}{r}\label{root:H_R}
    % rock
    \begin{dictentry}{HurRi}{n.}\label{word:HurRi}
        \dictdef*{
            rock
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{h}{t}\label{root:H_T}
    \begin{dictentry}{HaT}{n.}\label{word:HaT}
        \dictdef*{
            darkness
        }
    \end{dictentry}
    \begin{dictentry}{HiiT}{v.tr.}\label{word:HiiT}
        \dictdef{
            to darken, to shut out the light from, to shade
        }
        \dictdef{
            \textit{(of a dwelling)} to move out of \textit{smwh.}, to abandon
        }
        \dictdef{
            \textit{(of a place of business)} to close, to shut up
        }
    \end{dictentry}
    \begin{dictentry}{HiyaT}{v.intr.}\label{word:HiyaT}
        \dictdef{
            \textit{(impersonal)} to be dark out, to be murky
            \begin{quote}
                \famword{NaRKa-JaMJ fit RaTa iHuJa HiyaT.}\\
                \textit{`During the winter it's dark all day.'}
            \end{quote}
        }
        \dictdef{
            \textit{(of a dwelling)} to be abandoned, to have nobody home
        }
        \dictdef{
            \textit{(of a place of business)} to be closed, to be shut down, to not be accepting customers
        }
        \dictdef{
            \textit{(of a device)} to be turned off, to not be running, to not be in operation
        }
    \end{dictentry}
    \begin{dictentry}{iHaaT}{v.intr.}\label{word:iHaaT}
        \dictdef{
            to turn off, to cease emitting light
        }
        \dictdef{
            \textit{(impersonal)} to get dark, to stop being bright and sunny out
        }
        \dictdef{
            \textit{(of a place of business)} to close, to cease business, to shut down either for the day or in general
        }
        \dictdef{
            \textit{(of a device)} to turn off, to stop working
        }
    \end{dictentry}
    \begin{dictentry}{HiHiyaT}{v.tr.}\label{word:HiHiyaT}
        \dictdef*{
            to darken, to prevent from casting light, to put out \textit{(a torch or candle)}, to turn off \textit{(a lamp)}
        }
    \end{dictentry}
    \begin{dictentry}{aaHiT}{v.tr.}\label{word:aaHiT}
        \dictdef{
            \textit{(of a device)} to turn off, to shut down
        }
        \dictdef{
            \textit{(of a place of business)} to shut down, to close up, to end the operations of either for the day or in general
        }
    \end{dictentry}
    \begin{dictentry}{HaTa}{adj.}\label{word:HaTa}
        \dictdef{
            dark, without light
        }
        \dictdef{
            \textit{(of a dwelling)} abandoned, empty
        }
        \dictdef{
            \textit{(of a place of business)} closed, shut down
        }
        \dictdef{
            \textit{(of a device)} off, powered down, dead
        }
    \end{dictentry}
    \begin{dictentry}{HanaT}{n.}\label{word:HanaT}
        \dictdef*{
            the moon
        }
    \end{dictentry}
    \begin{dictentry}{iHuTa}{n.}\label{word:iHuTa}
        \dictdef*{
            night, nighttime
        }
    \end{dictentry}
    \begin{dictentry}{HuTi}{adj., n.}\label{word:HuTi}
        \dictdef*{
            black, the color black
        }
    \end{dictentry}
    \begin{dictentry}{HajuTa}{n.}\label{word:HajuTa}
        \dictdef*{
            curtains, shades, blinds
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{hc}{b}\label{root:HC_B}
    \begin{dictentry}{HeCanaB}{n.}\label{word:HCanaB}
        \dictdef*{
            hijabi, Muslim woman who wears a headscarf
        }
    \end{dictentry}
    \begin{dictentry}{HeCaBjalaB}{n.}\label{word:HCaBjalaB}
        \dictdef*{
            hijab, Muslim headscarf
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    J
%%%%%%%%%%%
\section*{J}

\begin{dictroot}{j}{b}\label{root:J_B}
    \begin{dictentry}{JaB}{n.}\label{word:JaB}
        \dictdef*{
            goodness, prosperity, good vibes, good luck
        }
    \end{dictentry}
    \begin{dictentry}{YiiB}{v.tr.}\label{word:YiiB}
        \dictdef{
            to treat \textit{sme.} well, to be kind to \textit{sme.}
        }
        \dictdef{
            to improve \textit{smth.}, to make \textit{smth.} better, to renovate \textit{smth.}, to overhaul \textit{smth.}, to spruce up
        }
    \end{dictentry}
    \begin{dictentry}{YiyaB}{v.intr.}\label{word:YiyaB}
        \dictdef*{
            to have good fortune, to be lucky
        }
    \end{dictentry}
    \begin{dictentry}{iYaaB}{v.intr.}\label{word:iYaaB}
        \dictdef*{
            to be good, to behave oneself, to do good deeds
        }
    \end{dictentry}
    \begin{dictentry}{YiYiyaB}{v.tr.}\label{word:YiYiyaB}
        \dictdef*{
            to bless \textit{sme.}, to bestow good fortune upon \textit{sme.}, to give \textit{sme.} a blessing
        }
    \end{dictentry}
    \begin{dictentry}{aaYiB}{v.tr.}\label{word:aaYiB}
        \dictdef*{
            to be a good influence on \textit{sme.}, to cause \textit{sme.} to behave well, to encourage \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{JaBa}{adj.}\label{word:JaBa}
        \dictdef*{
            good, fortunate, lucky, blessed
        }
    \end{dictentry}
    \begin{dictentry}{uYiBi}{adj.}\label{word:uYiBi}
        \dictdef*{
            happy, blessed, enthusiastic, amused
        }
    \end{dictentry}
    \begin{dictentry}{JanaB}{n.}\label{word:JanaB}
        \dictdef*{
            friend, buddy, pal, companion
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{JaBaila}{v.tr.}\label{word:JaBaila}
        \dictdef*{
            to like \textit{smth.}, to love \textit{smth.} \textit{(used of inanimate objects)}, to appreciate, to enjoy
            \begin{quote}
                \famword{CurKLi bus hwaJaBaila, iNaaMuc BiiN.}\\
                \textit{`He must love chocolate, he makes a habit of eating it.'}
            \end{quote}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{j}{l}\label{root:J_L}
    % many
    \begin{dictentry}{JaL}{n.}\label{word:JaL}
        \dictdef*{
            many, multitude, much, a large amount
        }
    \end{dictentry}
    \begin{dictentry}{JaLa}{adj.}\label{word:JaLa}
        \dictdef*{
            many, a lot of, quite a few
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{j}{mj}\label{root:J_MJ}
    % season
    \begin{dictentry}{JaMJ}{n.}\label{word:JaMJ}
        \dictdef*{
            season
        }
    \end{dictentry}
    %TODO: add the seasons of the traditional (and post-IE) 7a7a-FaM year
\end{dictroot}

\begin{dictroot}{j}{n}\label{root:J_N}
    \begin{dictentry}{YiiN}{v.tr.}\label{word:YiiN}
        \dictdef*{
            to take a break from \textit{smth.}, to take a vacation from \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{YiyaN}{v.intr.}\label{word:YiyaN}
        \dictdef*{
            to rest, to relax, to be resting, to destress
        }
    \end{dictentry}
    \begin{dictentry}{iYaaN}{v.intr.}\label{word:iYaaN}
        \dictdef{to wait}
        \dictdef{to lie down, to relax, to begin napping, to lie down with the intent to relax}
    \end{dictentry}
    \begin{dictentry}{YiYiyaN}{v.tr.}\label{word:YiYiyaN}
        \dictdef*{
            to relax \textit{sme.}, to calm \textit{sme.} down, to destress \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaYiN}{v.tr.}\label{word:aaYiN}
        \dictdef{
            to give \textit{sme.} a break, to give \textit{sme.} a vacation
        }
        \dictdef{
            to pause \textit{smth.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{j}{ps}\label{root:J_PS}
    % sibling (distance)
    \begin{dictentry}{JanaPS}{n.}\label{word:JanaPS}
        \dictdef{
            sibling considered less close than another sibling, for example due to large age gap or being step-siblings
        }
        \dictdef{
            cousin, child of parent's sibling
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{j}{s}\label{root:J_S}
    % god, spirit, ghost, holy, magical
    \begin{dictentry}{JaS}{n.}\label{word:JaS}
        \dictdef*{
            God
        }
    \end{dictentry}
    \begin{dictentry}{JaSa}{adj.}\label{word:JaSa}
        \dictdef{
            holy
        }
        \dictdef{
            magical
        }
    \end{dictentry}
    \begin{dictentry}{JanaS}{n.}\label{word:JanaS}
        \dictdef*{
            Jesus
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{j}{t}\label{root:J_T}
    % yeet, throw, travel
    \begin{dictentry}{YiiT}{v.tr.}\label{word:YiiT}
        \dictdef{
            to throw \textit{smth.}
        }
        \dictdef{
            to give \textit{smth.} (to someone)
            \begin{quote}
                \famword{nas LanaF daw CurKLi YiiT.}\\
                \textit{`I gave chocolates to my romantic partner.'}
            \end{quote}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{j}{w}\label{root:J_W}
    \begin{dictentry}{YiiW}{v.tr.}\label{word:YiiW}
        \dictdef*{to remember, to recall, to recollect}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{jp}{n}\label{root:JP_N}
    \begin{dictentry}{JPuuN}{n.}\label{word:JPuuN}
        \dictdef*{
            the Japanese people or ethnicity
        }
    \end{dictentry}
    \begin{dictentry}{JPaNia}{n.}\label{word:JPaNia}
        \dictdef*{
            Japan
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{jw}{rj}\label{root:JW_RJ}
    %Irish, Ireland
    \begin{dictentry}{JWaRJa}{adj.}\label{JWaRJa}
        \dictdef*{
            Irish, from Ireland
        }
    \end{dictentry}
    \begin{dictentry}{iYWuRJa}{n.}\label{word:iYWuRJa}
        \dictdef{
            Ireland, the island of Ireland in the British Isles upon which both the modern states of Ireland and Northern Ireland are located
        }
        \dictdef{
            \textit{(attested but considered incorrect)} the Republic of Ireland
        }
    \end{dictentry}
    \begin{dictentry}{JWuuRJ}{n.}\label{word:JWuuRJ}
        \dictdef*{
            Irish people, the Irish as a people group
        }
    \end{dictentry}
    \begin{dictentry}{JWaRYia}{n.}\label{word:JWaRJia}
        \dictdef*{
            the Republic of Ireland, Southern Ireland
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{NurKaw-iYWuRJa}{n.}\label{word:NurKaw-iYWuRJa}
        \dictdef*{
            Northern Ireland
            }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    K
%%%%%%%%%%%
\section*{K}

\begin{dictroot}{k}{j}
    % write
    \begin{dictentry}{KiiY}{v.tr.}
        \dictdef*{
            to write \textit{smth.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{k}
    % cookie, biscuit, cake?
    \begin{dictentry}{KuRKi}{n.}
        \dictdef*{
            small baked good, cookie, biscuit
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{l}
    \begin{dictentry}{\famwordold{}{k}{a}{l}{}}{n.}
        \dictdef*{
            humidity, wetness, dampness
            \begin{quote}
                \famwordold{i}{f}{u}{s}{a} \famwordold{}{j}{a}{b}{auru}, da \famwordold{}{l}{aju}{s}{a} \famwordold{}{k}{a}{l}{ila}\\
                \textit{`The house is lovely, but the floors are damp.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{k}{aa}{l}{}}{v.intr.}
        \dictdef{
            \textit{(impersonal)} to be a rainy day
            \begin{quote}
                \famwordold{waj}{h}{u}{j}{a} \famwordold{i}{k}{aa}{l}{}\\
                \textit{`Today's a rainy day.'}
            \end{quote}
        }
        \dictdef{
            \textit{(impersonal)} to be raining
            \begin{quote}
                \famwordold{i}{m}{u}{nt}{a} daw nas \famwordold{i}{j}{aa}{t}{e\lilglot} kaj da buse fit \famwordold{i}{k}{aa}{l}{}\\
                \textit{`I wanted to go to the mountains, but it's raining there.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{a}{l}{a}}{adj.}
        \dictdef{
            covered in water, saturated with water, wet, soaked
            \begin{quote}
                \famwordold{}{k}{a}{l}{a} \famwordold{m}{l}{i}{s}{} \famwordold{}{s}{a}{fr}{aariak}\\
                \textit{`Warm up your wet shoes.'}
            \end{quote}
        }
        \dictdef{
            fluid, liquid, melted
            \begin{quote}
                \famwordold{}{k}{asi}{l}{} \famwordold{}{k}{a}{l}{a} \famwordold{}{c}{ur}{kl}{iila}\\
                \textit{`The river was made of melted chocolate'}
                %KNUT PLEASE WEIGH IN ON THIS
                %I LIKE IT THIS IS GOOD -K
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{ur}{l}{i}}{n.}
        \dictdef*{the Earth, the globe}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{ar}{l}{i}}{n.}
        \dictdef*{
            liquid water, fresh water, water not part of a body of water or stream, water served as a beverage
            \begin{quote}
                mi \famwordold{}{n}{ar}{k}{a} \famwordold{}{k}{ar}{l}{iilali}?\\
                \textit{`Do you have any cold water?'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{asi}{l}{}}{n.}
        \dictdef{river, stream}
        \dictdef{
            stream or sprinkle of water, as from a faucet or tap
            \begin{quote}
                \famwordold{i}{s}{u}{n}{a} \famwordold{}{b}{a}{b}{a} \famwordold{}{k}{asi}{l}{ila}\\
                \textit{`The shower is low-flow'}\\
                (lit., \textit{`The shower has a mild stream'})
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{aju}{l}{a}}{n.}
        \dictdef{
            the surface of a body of water
            \begin{quote}
                naswi \famwordold{}{k}{aju}{l}{a} tui \famwordold{}{f}{ii}{l}{ami\lilglot} dak\\
                \textit{`We could see ourselves on the water's surface.'}
            \end{quote}
        }
        \dictdef{
            puddle
            \begin{quote}
                nas \famwordold{}{k}{aju}{l}{a} daw tui \famwordold{i}{l}{aa}{s}{}\\
                \textit{`I stepped in a puddle.'}
            \end{quote}
        }
        \dictdef{
            map
            \begin{quote}
                par \famwordold{}{k}{aju}{l}{a} \famwordold{}{sw}{uu}{t}{ilali}?\\
                \textit{`Is Switzerland on that map?'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{idi}{l}{}}{n.}
        \dictdef*{salt, sea salt}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{u}{l}{u}}{n.}
        \dictdef*{
            fish, fish-adjacent aquatic animal
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{u}{l}{i}}{adj., n.}
        \dictdef*{
            blue, the color blue
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{a}{k}{i}{l}{u}}{n.}
        \dictdef*{
            bottle
            \begin{quote}
                \textsc{mark} se kaj \famwordold{a}{k}{i}{l}{ulat} \famwordold{}{m}{ar}{h}{iila}\\
                \textit{`Mark owned five bottles of milk.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{imi}{l}{u}}{n.}
        \dictdef*{drinking glass}
    \end{dictentry}
    \begin{dictentry}{\famwordold{u}{k}{i}{l}{i}}{adj.}
        \dictdef{cold from being wet, soaked, shivering}
        \dictdef{\textit{(fig.)} anxious, uncomfortable, shaky}
    \end{dictentry}
    \begin{dictentry}{KuLaw}{n., adv.}
        \dictdef{
            east
        }
        \dictdef{
            eastwards, to the east, in the east
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{\famwordold{}{k}{asi}{l}{iri}}{v.intr.}
        \dictdef*{
            \textit{(euphemistic)} to pee
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{n}
    % to touch
    % to recognize
    \begin{dictentry}{KiiN}{v.tr.}
        \dictdef{
            to touch \textit{smth.} or \textit{sme.}
        }
        \dictdef{
            to recognize \textit{sme.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{p}
    % marriage, spouse
    \begin{dictentry}{KanaP}{n.}
        \dictdef{
            spouse, husband, wife, groom, bride, life partner
        }
        \dictdef{
            \textit{(-aj)} groom, husband
        }
        \dictdef{
            \textit{(-un)} wife, bride
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{pk}
    % fianc(e), engagement
    \begin{dictentry}{KanaPK}{n.}
        \dictdef{
            fianc, fiance
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{t}
    % Scotland, Scottish (from the Caits/Cats/Catts)
    \begin{dictentry}{KuuT}{n.}
        \dictdef{
            Scotland
        }
        \dictdef{
            the Scottish people
        }
    \end{dictentry}
    \begin{dictentry}{KarTi}{n.}
        \dictdef*{
            Scotch, Scotch whiskey
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{k}{w}
    \begin{dictentry}{\famwordold{}{k}{a}{w}{}}{n.}
        \dictdef*{growth}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{k}{aa}{w}{}}{v.intr.}
        \dictdef{to grow, to increase in size}
        \dictdef{to mature, to grow up, to reach maturity, to come of age}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{ii}{w}{}}{v.tr.}
        \dictdef{to plant \textit{smth.}, to sow \textit{smth.}}
        \dictdef{to conceive \textit{sme.}}
        \dictdef{\textit{(fig.)} to come up with \textit{smth.}, to conceive of \textit{smth.}, to think up \textit{smth.}}
    \end{dictentry}
    \begin{dictentry}{\famwordold{aa}{k}{i}{w}{}}{v.tr.}
        \dictdef{to grow \textit{smth.}, to tend \textit{smth.}, to raise \textit{smth.}}
        \dictdef{to raise \textit{sme.}, to care for \textit{sme.}, to read \textit{sme.}, to bring \textit{sme.} up}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{a}{w}{a}}{adj.}
        \dictdef{fully grown, mature, adult}
        \dictdef{grown-up, mature, serious}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{ana}{w}{}}{n.}
        \dictdef*{adult, grown up}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{ur}{w}{i}}{n.}
        \dictdef*{seed, bulb}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{ar}{w}{i}}{n.}
        \dictdef*{tea}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{k}{u}{w}{a}}{n.}
        \dictdef*{forest}
    \end{dictentry}
    \begin{dictentry}{\famwordold{m}{k}{i}{w}{}}{n.}
        \dictdef{stake, trellis, etc. used to support a growing plant}
        \dictdef{cane, walker, walking stick}
    \end{dictentry}
    \begin{dictentry}{\famwordold{in}{k}{i}{w}{}}{n.}
        \dictdef*{seedling, sapling, baby plant}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{uli}{w}{}}{n.}
        \dictdef*{shoulder}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{u}{w}{u}}{n.}
        \dictdef{frog, toad}
        \dictdef{\textit{(fig., slang)} smoker}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{asi}{w}{}}{n.}
        \dictdef{plant}
        \dictdef{tree}
        \dictdef{\textit{(fig.)} joint}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{aju}{w}{a}}{n.}
        \dictdef{leaf}
        \dictdef{\textit{(slang)} tobacco}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{idi}{w}{}}{n.}
        \dictdef{dried and/or powdered plant matter used for any purpose}
        \dictdef{ground tobacco or cannabis for smoking}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{u}{w}{i}}{adj., n.}
        \dictdef*{green, the color green}
    \end{dictentry}
    \begin{dictentry}{\famwordold{a}{k}{i}{w}{u}}{n.}
        \dictdef*{garden, greenhouse, arbor}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{k}{imi}{w}{u}}{n.}
        \dictdef*{pot, plot, planter}
    \end{dictentry}
    \begin{dictentry}{\famwordold{u}{k}{i}{w}{i}}{adj.}
        \dictdef*{feeling enriched, like one is growing as a person, self-fulfilled}
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{\famwordold{i}{k}{aa}{w}{ana}}{n.}
        \dictdef*{adolescent, teenager, older child}
    \end{dictentry}
    \begin{dictentry}{KaLa-KasiW}{n.}
        \dictdef*{
            cucumber
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{u}{k}{i}{w}{iisa}}{n.}
        \dictdef*{self-fulfillment, enrichment, personal growth}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{kr}{d}
    % grandparent-grandchild (distance)
    \begin{dictentry}{KRanaD}{n.}
        \dictdef{
            grandparent considered less close due to not being related by blood or otherwise
        }
        \dictdef{
            grandchild considered less close due to not being related by blood or otherwise
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    L
%%%%%%%%%%%
\section*{L}

\begin{dictroot}{l}{f}
    % to love (romantically)
    \begin{dictentry}{LiiF}{v.tr.}
        \dictdef*{
            to love \textit{sme.} romantically
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{l}{ks}
    %salmon
    \begin{dictentry}{LuKSu}{n.}
        \dictdef*{
            salmon
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{l}{s}
    %to walk
    \begin{dictentry}{LiiS}{v.tr.}
        to walk to \textit{smwh.}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{l}{t}
    \begin{dictentry}{\famwordold{}{l}{a}{t}{}}{n.}
        \dictdef*{trash, refuse, waste}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{l}{aa}{t}{}}{v.intr.}
        \dictdef*{to excrete, poop}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{l}{ii}{t}{}}{v.tr.}
        \dictdef*{to excrete \textit{smth.}}
    \end{dictentry}
    \begin{dictentry}{\famwordold{aa}{l}{i}{t}{}}{v.tr.}
        \dictdef*{to give \textit{sme.} the shits, cause stomach upset}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{l}{ur}{t}{i}}{n.}
        \dictdef*{feces, poo, a piece of poop}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{l}{ar}{t}{i}}{n.}
        \dictdef*{diarrhea, liquid shit}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{l}{u}{t}{a}}{n.}
        \dictdef{bathroom, outhouse}
        \dictdef{midden}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{l}{uli}{t}{}}{n.}
        \dictdef*{colon, lower intestines}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{l}{asi}{t}{}}{n.}
        \dictdef*{a long, skinny turd}
    \end{dictentry}
    \begin{dictentry}{\famwordold{a}{l}{i}{t}{u}}{n.}
        \dictdef{diaper}
        \dictdef{septic tank}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{l}{imi}{t}{u}}{n.}
        \dictdef*{toilet, toilet bowl}
    \end{dictentry}
    \begin{dictentry}{\famwordold{u}{l}{i}{t}{i}}{adj.}
        \dictdef{constipated}
        \dictdef{\textit{(fig.)} irritable, easily annoyed}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{l}{w}
    % high, top, above, rise/raise
    \begin{dictentry}{LaW}{n.}
        \dictdef*{
            the top, topside
        }
    \end{dictentry}
    \begin{dictentry}{LaWjalaW}{n.}
        \dictdef*{
            coat, jacket, sweater, etc.---any `topclothes' that cover the other clothing on the upper body
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{lh}{m}
    \begin{dictentry}{LeHaM}{n.}
        \dictdef*{
            doubt, question, suspicion
        }
    \end{dictentry}
    \begin{dictentry}{LeHiiM}{v.tr}
        \dictdef*{
            to doubt \textit{smth.}, to question \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{LeHiyaM}{v.intr.}
        \dictdef*{
            to be questioned, to be doubted, to be scrutinized
        }
    \end{dictentry}
    \begin{dictentry}{iLHaaM}{v.intr.}
        \dictdef*{
            to be suspicious, to feel suspicion about things, to be full of doubt
        }
    \end{dictentry}
    \begin{dictentry}{LeHiLHiyaM}{v.tr.}
        \dictdef*{
            to question \textit{sme.}, to interrogate \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaLHiM}{v.tr.}
        \dictdef*{
            to be suspicious to \textit{sme.}, to arouse \textit{sme.'s} suspicion
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{lj}{d}
    % listen, sound, loud, ear
    \begin{dictentry}{LYiiD}{v.tr.}
        \dictdef*{
            to listen to a sound
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    M
%%%%%%%%%%%
\section*{M}

\begin{dictroot}{m}{b}
    % slow
    \begin{dictentry}{MaBa}{adj.}
        \dictdef*{
            slow
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{c}
    %monkey -- something else as well maybe?
    \begin{dictentry}{MuCu}{n.}
        \dictdef*{
            monkey
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{h}
    \begin{dictentry}{MaH}{n.}
        \dictdef{
            name, moniker, title
            \begin{quote}
                \famword{wa aFiMu wan MaH BaJauru.}\\
                This book's title is bad.
            \end{quote}
        }
        \dictdef{
            brand, a mark on an item or piece of livestock to show ownership
            \begin{quote}
                \famword{[STAR] ha JENSEN carde wan MaHuru.}\\
                A star is Sir Jensen's brand.
            \end{quote}
        }
        \dictdef{
            \textit{(figurative)} brand, symbolic identity, the name or logo of a product or organization
            \begin{quote}
                \famword{nike MaH wan LuliS-CLurDi nas kaj.}\\
                I want Nike-brand shoes.
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{MiiH}{v.tr.}
        \dictdef{
            to be called \textit{smth.}, to be named \textit{smth.}, to go by \textit{smth.}
            \begin{quote}
                \famword{mi lis MiiHli?}\\
                What is your name?
            \end{quote}
        }
        \dictdef{
            to bear \textit{sme.'s} brand
            \begin{quote}
                \famword{MuHuaj ha JENSEN carde MiiH.}\\
                That bull bears Sir Jensen's brand.
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{MiyaH}{v.intr.}
        \dictdef*{
            to lactate, to produce milk
        }
    \end{dictentry}
    \begin{dictentry}{iMaaH}{v.intr.}
        \dictdef*{
            to call out one's name, to sound off
        }
    \end{dictentry}
    \begin{dictentry}{MiMiyaH}{v.tr}
        \dictdef*{
            to milk \textit{smth.}, to extract milk from \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaMiH}{v.tr.}
        \dictdef*{
            to name \textit{sme.}, to call \textit{sme.} by something
        }
        \dictdef{
            to call \textit{sme.'s} name out, to call on \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{MaHa}{adj.}
        \dictdef{
            said, aforementioned, named
            \begin{quote}
                \famword{MaHa FanaS \bigglot ana\bigglot uru.}\\
                The aforementioned person is a fool.
            \end{quote}
        }
        \dictdef{
            dairy, made from cow's milk
            \begin{quote}
                \famword{MaHa TaP nas NiiMe\lilglot{} dake\lilglot{} hwii.}\\
                \textit{`I can't eat any dairy.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{ManaH}{n.}
        \dictdef{
            milkmaid, dairy farmer
        }
        \dictdef{
            wet nurse
        }
    \end{dictentry}
    \begin{dictentry}{MurHi}{n.}
        \dictdef*{
            butter
        }
    \end{dictentry}
    \begin{dictentry}{MarHi}{n.}
        \dictdef{
            cow's milk
        }
        \dictdef{
            any milk or milk-like drink
        }
    \end{dictentry}
    \begin{dictentry}{iMuHa}{n.}
        \dictdef{
            dairy farm
        }
        \dictdef{
            \textit{(fig., slang)} titty bar
        }
    \end{dictentry}
    %\begin{dictentry}{mMiH}{n.}
    %    \dictdef*{}
    %\end{dictentry}
    \begin{dictentry}{inMiH}{n.}
        \dictdef{
            calf, baby cow
        }
        \dictdef{
            \textit{(fig., slang)} small breasts
        }
    \end{dictentry}
    \begin{dictentry}{MuliH}{n.}
        \dictdef*{
            breast, tit, udder, teat
        }
    \end{dictentry}
    \begin{dictentry}{MuHu}{n.}
        \dictdef{
            cow, head of cattle
        }
        \dictdef{
            \textit{(fig., slang)} stripper, busty woman
        }\footnote{Disclaimer: this was sparky's idea}
    \end{dictentry}
    \begin{dictentry}{MasiH}{n.}
        \dictdef*{
            stick of ice cream, ice pop
        }
    \end{dictentry}
    \begin{dictentry}{MajuHa}{n.}
        \dictdef*{
            sign, nameplate
        }
    \end{dictentry}
    \begin{dictentry}{MidiH}{n.}
        \dictdef{
            powdered milk, milk powder
        }
        \dictdef{
            baby formula
        }
    \end{dictentry}
    \begin{dictentry}{MuHi}{adj., n.}
        \dictdef*{
            cream-colored, the color cream, off-white
        }
    \end{dictentry}
    \begin{dictentry}{aMiHu}{n.}
        \dictdef*{
            milk carton
        }
    \end{dictentry}
    \begin{dictentry}{MimiHu}{n.}
        \dictdef*{
            baby bottle
        }
    \end{dictentry}
    \begin{dictentry}{uMiHi}{adj.}
        \dictdef{
            warm and cozy, completely safe and secure (as if being nursed by one's mother as a baby)
        }
        \dictdef{
            milk drunk, in a food coma
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{MarHibin}{n}
        \dictdef*{
            cream, milk fat
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{l}
    % dirty, sick
    \begin{dictentry}{MaLa}{adj.}
        \dictdef{
            unhealthy, ill
        }
        \dictdef{
            dirty
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{m}
    %parent-child (close)
    %BUT ALSO to joke, to make fun of
    \begin{dictentry}{MaM}{n.}
        \dictdef*{
            joke
        }
    \end{dictentry}
    \begin{dictentry}{MiiM}{v.tr.}
        \dictdef*{
            to joke about \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{MaMa}{adj.}
        \dictdef{
            funny
        }
        \dictdef{
            parental
        }
    \end{dictentry}
    \begin{dictentry}{ManaM}{n.}
        \dictdef{
            mother, father, parent
        }
        \dictdef{
            daughter, son, child
        }
        \dictdef{
            comedian
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{n}
    % culture
    \begin{dictentry}{MaN}{n.}
        \dictdef*{
            culture
        }
    \end{dictentry}
    \begin{dictentry}{MaNa}{adj.}
        \dictdef*{
            cultured, mannered
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{nt}
    %tall, mountain, long on the natural axis of measurement
    \begin{dictentry}{MiiNT}{v.tr.}
        \dictdef*{
            to place importance on \textit{smth.}, to care about \textit{smth.}, to have \textit{smth.} be important to oneself
        }
    \end{dictentry}
    \begin{dictentry}{MiyaNT}{v.intr.}
        \dictdef*{
            to matter, to be important
        }
    \end{dictentry}
    \begin{dictentry}{iMaaNT}{v.intr.}
        \dictdef*{
            to care, to give a shit
        }
    \end{dictentry}
    \begin{dictentry}{MiMiyaNT}{v.tr.}
        \dictdef*{
            to elevate, to emphasize, to focus on \textit{smth.}, to have \textit{smth.} as one's theme or thesis
        }
    \end{dictentry}
    \begin{dictentry}{aaMiNT}{v.tr.}
        \dictdef*{
            to convince \textit{sme.}, to make \textit{sme.} care, to make \textit{sme.} aware (of something)
        }
    \end{dictentry}
    \begin{dictentry}{MaNTa}{adj.}
        \dictdef{
            large, long, tall, wide, of great proportion in its natural axis of measurement
        }
        \dictdef{
            important, grave
        }
    \end{dictentry}
    \begin{dictentry}{MuNTaw}{n., adv.}
        \dictdef{
            west
        }
        \dictdef{
            westwards, to the west, in the west
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{rk}
    %America -- iMuRKa for continents, MaRKia for USA
    %MuuRK = NatAm?
    \begin{dictentry}{iMuRKa}{n.}
        \dictdef*{
            the Americas
        }
    \end{dictentry}
    \begin{dictentry}{MuuRK}{n.}
        \dictdef*{
            Native American people
        }
    \end{dictentry}
    \begin{dictentry}{MaRKia}{n.}
        \dictdef*{
            the United States of America
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{m}{w}
    % game
    \begin{dictentry}{MaW}{n.}
        \dictdef*{
            game
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{mk}{f}
    \begin{dictentry}{MeKiiF}{v.tr.}
        \dictdef*{
            to knot up \textit{smth.}, to tie a knot in \textit{smth.}
            \begin{quote}
                \famword{MeKasiF ha \textrm{K}NUT MeKiiF}\\
                \textit{`Knut tied a knot in the rope.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{MeKiyaF}{v.intr.}
        \dictdef{to be tied in knots, to be knotted up, to be tangled}
        \dictdef{to be knitted, to be made by forming interconnected knots}
        \dictdef{\textit{(of a situation)} to be complicated, to be overly complex, to be hard to deal with}
    \end{dictentry}
    \begin{dictentry}{iMKaaF}{v.intr.}
        \dictdef{to tie a knot, to tie knots in something, to tangle stuff up}
        \dictdef{to knit something, to knit stuff, to do knitting}
        \dictdef{to obstruct things, to get in the way, to tangle things up}
    \end{dictentry}
    \begin{dictentry}{MeKiMKiyaF}{v.tr.}
        \dictdef{to make \textit{smth.} by knitting, to knit \textit{smth.}}
        \dictdef{to overcomplicate, to cause \textit{smth.} to become complicated and hard to deal with}
    \end{dictentry}
    \begin{dictentry}{MeKurFi}{n.}
        \dictdef*{knot}
    \end{dictentry}
    \begin{dictentry}{MeKasiF}{n.}
        \dictdef*{rope, yarn}
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    N
%%%%%%%%%%%
\section*{N}

\begin{dictroot}{n}{jd}
    \begin{dictentry}{\famwordold{}{n}{a}{jd}{}}{n.}
        \dictdef*{solitude}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{n}{aa}{jd}{}}{v.intr.}
       \dictdef{to get separated, to get left alone}
       \dictdef{to get left behind}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ii}{yd}{}}{v.tr.}
        \dictdef{to separate \textit{sme.} from a group}
        \dictdef{to isolate \textit{smth.} from out of a mixture}
        \dictdef{to single out, highlight, emphasize \textit{smth.}}
    \end{dictentry}
    \begin{dictentry}{\famwordold{aa}{n}{i}{yd}{}}{v.tr.}
        \dictdef*{to exclude \textit{smth.} or \textit{sme.}}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{a}{jd}{a}}{adj.}
        \dictdef{only, solely}
        \dictdef{lone, single}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ana}{jd}{}}{n.}
        \dictdef*{outcast}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{n}{u}{jd}{a}}{n.}
        \dictdef*{isolated area}
    \end{dictentry}
    \begin{dictentry}{\famwordold{u}{n}{i}{yd}{i}}{n.}
        \dictdef*{lonely}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{n}{kl}
    % aunt/uncle-niece/nephew
    \begin{dictentry}{NanaKL}{n.}
        \dictdef{
            aunt, uncle, parent's sibling
        }
        \dictdef{
            niece, nephew, sibling's child
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{n}{m}
    \begin{dictentry}{\famwordold{}{n}{a}{m}{}}{n.}
        \dictdef{food, meal, sustenance}
        \dictdef{\textit{(fig.)} fuel}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{n}{aa}{m}{}}{v.intr.}
        \dictdef*{to eat \textit{(intr.)}}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ii}{m}{}}{v.tr.}
        \dictdef*{to eat \textit{smth.}}
    \end{dictentry}
    \begin{dictentry}{\famwordold{aa}{n}{i}{m}{}}{v.tr.}
        \dictdef{%
            to feed \textit{sme.}
            \begin{quote}
                nas \famwordold{in}{b}{i}{\bigglot}{ini} \famwordold{}{p}{ur}{l}{i} fun \famwordold{aa}{n}{i}{m}{}\\
                \textit{`I fed my littlest sibling an apple.'}
            \end{quote}
        }
        \dictdef{\textit{(lit. or fig.)} to satisfy \textit{sme.}, to sate \textit{sme./smth.} }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{a}{m}{a}}{adj.}
        \dictdef*{satisfying, filling, tasty}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ana}{m}{}}{n.}
        \dictdef{%
            chef, cook
            \begin{quote}
                \famwordold{}{n}{ana}{m}{} daw, \famwordold{}{n}{a}{m}{} \famwordold{}{j}{a}{b}{auru\lilglot} lituc \famwordold{}{f}{ii}{m}{ak}\\
                \textit{`Compliments to the chef.' (\emph{lit.,} `Tell the chef the meal was very good.')}
            \end{quote}%
            }
        \dictdef{%
            feeder, one who feeds (and potentially otherwise cares for) someone or something, -sitter.
            \begin{quote}
                nemi \famwordold{}{c}{u}{s}{u} wan \famwordold{}{n}{ana}{m}{} \famwordold{aa}{t}{i}{lw}{} tuuq\\
                \textit{`We have to hire someone to feed the cat.'}
            \end{quote}
            }
        \dictdef{%
            fulfiller, provider, satisfier
            \begin{quote}
                \famwordold{}{f}{ana}{s}{aj} \famwordold{a}{m}{i}{m}{u} wan \famwordold{}{n}{ana}{m}{uru\lilglot} tuuquc nas wan \famwordold{}{m}{ana}{m}{} \famwordold{}{f}{ii}{m}{}\\
                \textit{`My mother says that a man must be his family's provider.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ur}{m}{i}}{n.}
        \dictdef*{food}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ar}{m}{i}}{n.}
        \dictdef*{soup}
    \end{dictentry}
    \begin{dictentry}{\famwordold{i}{n}{u}{m}{a}}{n.}
        \dictdef*{%
            kitchen, dining room
            \begin{quote}
                \famwordold{}{m}{ana}{m}{} \famwordold{}{r}{a}{t}{a} \famwordold{i}{h}{u}{j}{a} fit \famwordold{i}{n}{u}{m}{a} fituru.\\
                \textit{`Mother has been in the kitchen all day.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{\famwordold{m}{n}{i}{m}{}}{n.}
        \dictdef*{eating or cooking utensil}
    \end{dictentry}
    \begin{dictentry}{\famwordold{in}{n}{i}{m}{}}{n.}
        \dictdef*{snack, morsel}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{uli}{m}{}}{n.}
        \dictdef{
            mouth
            \begin{quote}
                \famwordold{}{k}{ur}{k}{i} \famwordold{}{n}{uli}{m}{} daw fit nas \famwordold{aa}{pl}{i}{s}{}\\
                \textit{`I put the cookie in my mouth.'}
            \end{quote}
            }
        \dictdef{
            teeth
            \begin{quote}
                \famwordold{}{n}{uli}{m}{} mi \famwordold{i}{s}{aa}{j}{uc} fidul \famwordold{}{s}{ii}{n}{ak}!\\
                \textit{`Brush your teeth before bed!'}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{u}{m}{u}}{n.}
        \dictdef*{locust}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{asi}{m}{}}{n.}
        \dictdef*{chopsticks}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{aju}{m}{a}}{n.}
        \dictdef*{plate, platter, surface for eating}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{idi}{m}{}}{n.}
        \dictdef*{ground spice or seasoning}
    \end{dictentry}
    \begin{dictentry}{\famwordold{a}{n}{i}{m}{u}}{n.}
        \dictdef*{jar}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{imi}{m}{u}}{n.}
        \dictdef*{bowl}
    \end{dictentry}
    \begin{dictentry}{\famwordold{u}{n}{i}{m}{i}}{adj.}
        \dictdef*{hungry}
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{\famwordold{in}{f}{i}{s}{}\famwordold{}{n}{ana}{m}{}}{n.}
        \dictdef*{babysitter, nanny}
    \end{dictentry}
    \begin{dictentry}{\famwordold{m}{n}{i}{m}{aj}}{n.}
        \dictdef*{spoon}
    \end{dictentry}
    \begin{dictentry}{\famwordold{m}{n}{i}{m}{un}}{n.}
        \dictdef*{fork}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{a}{m}{anara}}{int.}
        \dictdef*{bon appetit, have a nice meal}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{n}{ar}{m}{ibin}}{n.}
        \dictdef*{stew}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{f}{a}{s}{a}-\famwordold{}{n}{a}{m}{}}{n.}
        \dictdef*{breakfast, morning meal}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{h}{a}{j}{a}-\famwordold{}{n}{a}{m}{}}{n.}
        \dictdef*{lunch, midday meal}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{h}{a}{t}{a}-\famwordold{}{n}{a}{m}{}}{n.}
        \dictdef*{midnight snack}
    \end{dictentry}
    \begin{dictentry}{\famwordold{}{s}{a}{j}{a}-\famwordold{}{n}{a}{m}{}}{n.}
        \dictdef*{dinner, supper, evening meal}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{n}{rk}
    %cold, Norway
    \begin{dictentry}{NaRKa}{adj.}
        \dictdef{
            cold
        }
        \dictdef{
            Norwegian
        }
    \end{dictentry}
    \begin{dictentry}{NuuRK}{n.}
        \dictdef{
            Norway
        }
        \dictdef{
            the Norwegian people
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{n}{w}
    %die, death
    \begin{dictentry}{NaW}{n.}
        \dictdef*{
            death
        }
    \end{dictentry}
    \begin{dictentry}{NiiW}{v.tr.}
        \dictdef*{
            to murder \textit{sme.}, to kill \textit{sme.} (intentionally)
        }
    \end{dictentry}
    \begin{dictentry}{NiyaW}{v.intr.}
        \dictdef*{
            to die
        }
    \end{dictentry}
    \begin{dictentry}{NiNiyaW}{v.tr.}
        \dictdef*{
            to cause \textit{sme.} to die, to kill \textit{sme.} (with or without intention), to be the means of one's demise
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    P
%%%%%%%%%%%
\section*{P}

\begin{dictroot}{p}{d}
    \begin{dictentry}{PaD}{n.}
        \dictdef*{
            liter, 1000 milliliters, pot \textit{(derived from Danish `pot')}
        }
    \end{dictentry}
    \begin{dictentry}{inPiD}{n.}
        \dictdef*{
            pint,  liter, 250 milliliters,  pot
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{inPiDini}{n.}
        \dictdef{
            milliliter
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{p}{l}
    \begin{dictentry}{PaL}{n.}
        \dictdef{
            fertility, fruitfulness
        }
        \dictdef{
            plenty, abundance of some desired thing or quality
        }
    \end{dictentry}
    \begin{dictentry}{PiiL}{v.tr.}
        \dictdef*{
            to result in \textit{smth.}, to produce \textit{smth.}, to bear
        }
    \end{dictentry}
    \begin{dictentry}{PiyaL}{v.intr.}
        \dictdef*{
            to bear fruit, \textit{(of a method or tool)} to produce results
        }
    \end{dictentry}
    \begin{dictentry}{iPaaL}{v.intr.}
        \dictdef*{
            \textit{(of a person)} to get results, to be effective at producing positive outcomes
        }
    \end{dictentry}
    \begin{dictentry}{PiPiyaL}{v.tr.}
        \dictdef*{
            to cause \textit{smth.} to bear fruit, to fertilize, to cause \textit{a method or tool} to produce results
        }
    \end{dictentry}
    \begin{dictentry}{aaPiL}{v.tr.}
        \dictdef*{
            to get results from \textit{sme.}, to motivate \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{PaLa}{adj.}
        \dictdef{
            fruitful, fertile
        }
        \dictdef{
            plentiful, abundant
        }
    \end{dictentry}
    \begin{dictentry}{PanaL}{n.}
        \dictdef*{
            a hard worker, an overachiever, someone who gets results
        }
    \end{dictentry}
    \begin{dictentry}{PurLi}{n.}
        \dictdef{
            fruit, vegetable, nut, the edible product of a plant
        }
        \dictdef{
            apple, the fruit of \textit{Malus domestica} specifically
        }
        \dictdef{
            \emph{(fig.)} end result, effect, consequence
        }
    \end{dictentry}
    \begin{dictentry}{ParLi}{n.}
        \dictdef*{
            juice, fruit juice
        }
    \end{dictentry}
    \begin{dictentry}{iPuLa}{n.}
        \dictdef{
            orchard, plantation, fruit farm
        }
    \end{dictentry}
    \begin{dictentry}{mPiL}{n.}
        \dictdef{
            fertilizer, substance intended to improve the amount of fruit born by a plant
        }
        \dictdef{
            any device or substance intended to promote human fertility
        }
        \dictdef{
            any device or substance intended to increase the output of a method or tool
        }
    \end{dictentry}
    \begin{dictentry}{inPiL}{n.}
        \dictdef*{
            berry, nut, small fruit
        }
    \end{dictentry}
    \begin{dictentry}{PuliL}{n.}
        \dictdef{
            womb, female reproductive system
        }
        \dictdef{
            \textit{(botany)} the fruit-producing part of a flower, pistil, ovaries \textit{(of a plant)}
        }
    \end{dictentry}
    %\begin{dictentry}{\famwordold{}{p}{u}{l}{u}}{n.}
    %    \dictdef*{squirrel}
    %\end{dictentry}
    \begin{dictentry}{PasiL}{n.}
        \dictdef*{
            long, slender fruit or vegetable (e.g., cucumber, eggplant, zucchini, yellow squash); cucumiform
        }
    \end{dictentry}
    \begin{dictentry}{PidiL}{n.}
        \dictdef*{
            solute, the component that is dissolved into some solvent to form a solution
        }
    \end{dictentry}
    \begin{dictentry}{PuLi}{adj., n.}
        \dictdef*{
            red, reddish-pink, the color red/reddish-pink
        }
    \end{dictentry}
    \begin{dictentry}{aPiLu}{n.}
        \dictdef*{
            jar, can
        }
    \end{dictentry}
    \begin{dictentry}{PimiLu}{n.}
        \dictdef*{
            basket
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{SaH-PurLi}{n.}
        \dictdef*{
            onion, onion bulb
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{p}{n}
    % bread
    \begin{dictentry}{PurNi}{n.}
        \dictdef{
            loaf of bread
        }
        \dictdef{
            bread roll?
        }
    \end{dictentry}
    \begin{dictentry}{PasiN}{n.}
        \dictdef*{
            baguette
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{p}{s}
    % piss
    \begin{dictentry}{iPaaS}{v.intr.}
        \dictdef{
            to piss, to urinate, to pee
        }
    \end{dictentry}
    \begin{dictentry}{ParSi}{n.}
        \dictdef*{
            urine
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{pl}{d}
    % swim
    \begin{dictentry}{iPLaaD}{v.intr.}
        \dictdef*{
            to swim with one's body completely submerged in water, as done by a fish, scuba diver, or submarine
        }
    \end{dictentry}
    \begin{dictentry}{PLuDu}{n.}
        \dictdef{
            fish, aquatic non-mammalian vertebrate
        }
        \dictdef{
            any sea creature that swims completely submerged in water
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{pl}{s}
    \begin{dictentry}{PLaS}{n.}
        \dictdef*{self-propelled motion, movement}
    \end{dictentry}
    \begin{dictentry}{PLiiS}{v.tr.}
        \dictdef*{to move (oneself) to \textit{smwh.}, to go to \textit{smwh.}}
    \end{dictentry}
    \begin{dictentry}{PLiyaS}{v.intr.}
        \dictdef*{
            to be located \textit{(smwh.)}, to be present \textit{(smwh.)}
        }
    \end{dictentry}
    \begin{dictentry}{iPLaaS}{v.intr.}
        \dictdef*{to dwell, to settle \textit{(in some location)}, to establish one's home}
    \end{dictentry}
    \begin{dictentry}{PLiPLiyaS}{v.tr.}
        \dictdef{
            to place \textit{smth.} \textit{(smwh.)}
        }
        \dictdef{
            to establish \textit{smth.} \textit{(smwh.)}, to build \textit{smth.} \textit{(smwh.)}, to set \textit{smth.} up \textit{(smwh.)}
        }
    \end{dictentry}
    \begin{dictentry}{aaPLiS}{v.tr.}
        \dictdef{
            to cause \textit{sme.} to move (themselves) \textit{(smwh.)}
        }
        \dictdef{
            to cause \textit{sme.} to settle down \textit{(smwh.)}, to set \textit{sme.} up (with a place to live or job)
        }
    \end{dictentry}
    \begin{dictentry}{PLanaS}{n.}
        \dictdef{driver, chauffeur}
        \dictdef{mover, hauler}
    \end{dictentry}
    \begin{dictentry}{PLarSi}{n.}
        \dictdef{gasoline}
        \dictdef{\textit{(slang)} coffee}
    \end{dictentry}
    \begin{dictentry}{iPLuSa}{n.}
        \dictdef{place, location}
        \dictdef{stop, station, terminal}
    \end{dictentry}
    \begin{dictentry}{mPLiS}{n.}
        \dictdef*{mode of transportation}
    \end{dictentry}
    \begin{dictentry}{PLuSu}{n.}
        \dictdef{car, motor vehicle, automobile}
        \dictdef{\textit{(dated)} mount, ridden animal}
    \end{dictentry}
    \begin{dictentry}{PLasiS}{n.}
        \dictdef*{line, row}
    \end{dictentry}
    \begin{dictentry}{PLajuSa}{n.}
        \dictdef*{layer}
    \end{dictentry}
    \begin{dictentry}{PLidiS}{n.}
        \dictdef*{\textit{(slang)} cocaine}
    \end{dictentry}
    \begin{dictentry}{aPLiSu}{n.}
        \dictdef*{engine}
    \end{dictentry}
    \begin{dictentry}{PLimiSu}{n.}
        \dictdef*{generic container, bin, box}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{pr}{l}
    \begin{dictentry}{PRiiL}{v.tr.}
        \dictdef*{to forget \textit{smth.}, to have \textit{smth.} slip one's mind}
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    Q
%%%%%%%%%%%
\section*{Q}

\begin{dictroot}{q}{\bigglot}
    % to believe, opine, conclude
    \begin{dictentry}{iQaa\bigglot}{n.}
        \dictdef*{
            to think, believe, be of the opinion of
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{q}{h}
    \begin{dictentry}{QiiH}{v.tr.}
        \dictdef*{
            to weave in and out of \textit{smth.}, to move through by turning and twisting, to make ones way through \textit{smth.} by winding in and out or from side to side
            }
    \end{dictentry}
    \begin{dictentry}{QiyeH}{v.intr.}
        \dictdef{
            to be woven, to be made to weave in and out of something, to be twisted and turned around something
            \begin{quote}
                \famword{TBD}//
                \textit{A strand of grass was woven in her hair.}
            \end{quote}
        }
        \dictdef{
            to be formed by weaving things together, to be woven
            \begin{quote}
                \famword{TBD}//
                \textit{This cloth was woven 100 years ago.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{iQaaH}{v.intr.}
        \dictdef*{
            to dodge and weave, to move back and forth in a serpentine manner
        }
    \end{dictentry}
    \begin{dictentry}{QiQiyaH}{v.tr.}
        \dictdef{
            to weave \textit{smth.} together, to cause \textit{smth.} to be woven together
            \begin{quote}
                \famword{TBD}\\
                \textit{He wove the threads together to make a blanket.}
            \end{quote}
        }
        \dictdef{
            to weave \textit{smth.}, to create \textit{smth.} by weaving
            \begin{quote}
                \famword{TBD}\\
                \textit{My grandmother wove me this sweater.}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{QajuHa}{n.}
        \dictdef*{
            fabric, cloth, woven fabric, cloth
        }
    \end{dictentry}
    \begin{dictentry}{QuHu}{n.}
        \dictdef*{lizard, reptile}
    \end{dictentry}
    \begin{dictentry}{QasiH}{n.}
        \dictdef*{snake}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{q}{r}
    %squirrel
    \begin{dictentry}{QuRu}{n.}
        \dictdef*{
            squirrel
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{q}{st}
    % barley
    \begin{dictentry}{QurSTi}{n.}
        \dictdef*{
            barley grain
        }
    \end{dictentry}
    \begin{dictentry}{iQuSTa}{n.}
        \dictdef*{
            barley field
        }
    \end{dictentry}
    \begin{dictentry}{QasiST}{n.}
        \dictdef*{
            stalk of barley
        }
    \end{dictentry}
    \begin{dictentry}{QidiST}{n.}
        \dictdef*{
            barley flour
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    R
%%%%%%%%%%%
\section*{R}

\begin{dictroot}{r}{\bigglot}
    % rule, law
    \begin{dictentry}{Ra\bigglot}{n.}
        \dictdef{
            rule, commandment, law, ordinance
        }
        \dictdef{
            law, justice, set of rules by which society runs
        }
    \end{dictentry}
    \begin{dictentry}{Rana\bigglot}{n.}
        \dictdef*{
            legislator, judge, lawmaker, legislative representative
        }
    \end{dictentry}
    \begin{dictentry}{iRu{\bigglot}a}{n.}
        \dictdef*{
            legislature
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{r}{kd}
    % wood
    \begin{dictentry}{RurKDi}{n.}
        \dictdef*{
            piece of wood
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{r}{m}
    \begin{dictentry}{RiiM}{v.tr.}
        \dictdef*{
            to hold \textit{smth.}, carry \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{RiyaM}{v.intr.}
        \dictdef*{
            to be held, to be grasped, to be kept
            }
    \end{dictentry}
    \begin{dictentry}{RiRiyaM}{v.tr.}
        \dictdef*{
            to hand \textit{smth.} (to \textit{sme.}), to hand \textit{smth.} over, to pass \textit{smth.} (to \textit{sme.})
        }
    \end{dictentry}
    \begin{dictentry}{aaRiM}{v.tr.}
        \dictdef*{
            to grab \textit{smth.}, to grasp \textit{smth.}, to take hold of \textit{smth.}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{r}{q}
    \begin{dictentry}{RaQ}{n.}
        \dictdef{pain}
        \dictdef{strike, blow}
    \end{dictentry}
    \begin{dictentry}{RiiQ}{v.tr.}
        \dictdef{
            to attack \textit{sme.}, to strike \textit{sme.}, to hit \textit{sme.}, to try to injure \textit{sme.} with volition, to try to hurt \textit{sme.} deliberately
            \begin{quote}
                \famword{TBD}\\
                \textit{`Magnus's dog attacked me!'}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{RiyaQ}{v.intr.}
        \dictdef*{
            \textit{(of a person)} to suffer, to be in pain, to be injured
            \begin{quote}
                \famword{TBD}\\
                \textit{`The sick old woman is in a lot of pain.'}
            \end{quote}
            }
    \end{dictentry}
    \begin{dictentry}{iRaaQ}{v.intr}
        \dictdef*{
            to cause harm through presence or inaction, to be harmful, to cause injury without volition
            \begin{quote}
                \famword{TBD}\\
                \textit{`A blow to the head really hurts.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{RiRiyaQ}{v.tr.}
        \dictdef*{
            \textit{(of a body part, reflexive)} to hurt \textit{(sme.)}, to be injured, to cause pain
            \begin{quote}
                \famword{BuliT nas RiRiyaQami}\\
                \textit{`My head hurts.'}
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{aaRiQ}{v.tr.}
        \dictdef*{
            to hurt \textit{sme.}, to inflict pain on \textit{sme.} but without volition, to cause pain or injury to \textit{sme.} through inaction or mere presence
            \begin{quote}
                FanaS MarHi aaRiQibitu nas FanaSuru.\\
                \textit{`I am lactose-intolerant.'}\\
                (lit., \textit{`I am a person who milk hurts.'})
            \end{quote}
        }
    \end{dictentry}
    \begin{dictentry}{RaQa}{adj.}
        \dictdef*{painful, hurtful, injurous}
    \end{dictentry}
    \begin{dictentry}{RanaQ}{n.}
        \dictdef*{attacker, fighter, injurer}
    \end{dictentry}
    \begin{dictentry}{mRiQ}{n.}
        \dictdef*{weapon}
    \end{dictentry}
    \begin{dictentry}{RuQi}{adj., n.}
        \dictdef*{red, the color red}
    \end{dictentry}
    \begin{dictentry}{uRiQi}{adj.}
        \dictdef*{hurt, hurting, in pain, injured}
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{uRiQiana}{n.}
        \dictdef*{victim, injured person}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{r}{r}
    % strange, weird, bizarre
    \begin{dictentry}{RaRa}{adj.}
        \dictdef*{
            weird, strange, bizarre
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{r}{t}
    % cycle, year, wheel, whole
    \begin{dictentry}{RaT}{n.}
        \dictdef{
            cycle, circle, lap, revolution
        }
        \dictdef{
            year
        }
        \dictdef{
            \textit{(of a game)} round, game
        }
        \dictdef{
            conclusion
        }
    \end{dictentry}
    \begin{dictentry}{RiiT}{v.tr.}
        \dictdef*{
            to complete, finish \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{RiyaT}{v.intr.}
        \dictdef{
            to move in a circle, orbit around a central point
        }
        \dictdef{
            \textit{(of an event)} to conclude, finish, cycle
        }
    \end{dictentry}
    \begin{dictentry}{iRaaT}{v.intr.}
        \dictdef*{
            to rotate around one's own axis
        }
    \end{dictentry}
    \begin{dictentry}{RiRiyaT}{v.tr.}
        \dictdef{
            to have \textit{smth.} orbit one's own location, to be the central point around which something orbits
        }
        \dictdef{
            \textit{(fig.)} to be the center of attention, seek to have influence over everything
        }
    \end{dictentry}
    \begin{dictentry}{aaRiT}{v.tr.}
        \dictdef*{
            to spin \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{RaTa}{adj.}
        \dictdef*{
            whole, entire, complete
        }
    \end{dictentry}
    \begin{dictentry}{RanaT}{n.}
        \dictdef*{
            ???
        }
    \end{dictentry}
    \begin{dictentry}{RurTi}{n.}
        \dictdef*{
            wheel
        }
    \end{dictentry}
    \begin{dictentry}{iRuTa}{n.}
        \dictdef*{
            roundabout, traffic circle
        }
    \end{dictentry}
    \begin{dictentry}{mRiT}{n.}
        \dictdef*{
            turntable
        }
    \end{dictentry}
    \begin{dictentry}{inRiT}{n.}
        \dictdef{
            section, part of cycle or lap
        }
        \dictdef{
            \textit{(of a game)} a person's turn
        }
    \end{dictentry}
    \begin{dictentry}{RuliT}{n.}
        \dictdef*{
            uterine lining
        }
    \end{dictentry}
    \begin{dictentry}{RuTu}{n.}
        \dictdef*{
            roly poly, potato bug, woodlouse
        }
    \end{dictentry}
    \begin{dictentry}{RasiT}{n.}
        \dictdef*{
            axis, axle, shaft
        }
    \end{dictentry}
    \begin{dictentry}{RajuTa}{n.}
        \dictdef*{
            calendar, timetable
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{rt}{s}
    \begin{dictentry}{ReTaSa}{adj.}
        \dictdef{
            nude, bare, naked
        }
        \dictdef{
            just, merely, only
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    S
%%%%%%%%%%%
\section*{S}

\begin{dictroot}{s}{fr}
    % hot
    \begin{dictentry}{SaFR}{n.}
        \dictdef*{
            heat
        }
    \end{dictentry}
    \begin{dictentry}{SiiFR}{v.tr.}
        \dictdef*{
            to cook, bake, boil \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{SiyaFR}{v.intr.}
        \dictdef*{
            \textit{(mediopassive)} to cook, bake, boil
        }
    \end{dictentry}
    \begin{dictentry}{iSaaFR}{v.intr.}
        \dictdef*{
            to make food, prepare food
        }
    \end{dictentry}
    \begin{dictentry}{SiSiyaFR}{v.tr.}
        \dictdef*{
            \textit{(of a cooking apparatus)} to cook, bake, boil \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaSiFR}{v.tr.}
        \dictdef*{
            \textit{(of foodstuff)} to entice \textit{sme.} into eating or preparing food
        }
    \end{dictentry}
    \begin{dictentry}{SaFRa}{adj.}
        \dictdef{
            hot, warm
        }
        \dictdef{
            spicy
        }
    \end{dictentry}
    \begin{dictentry}{SanaFR}{n.}
        \dictdef*{
            cook, chef
        }
    \end{dictentry}
    \begin{dictentry}{SurFRi}{n.}
        \dictdef*{
            coal, embers
        }
    \end{dictentry}
    \begin{dictentry}{SarFRi}{n.}
        \dictdef{
            hot beverage, coffee, tea
        }
        \dictdef{
            \textit{(colloquial)} lava
        }
    \end{dictentry}
    \begin{dictentry}{iSuFRa}{n.}
        \dictdef*{
            desert
        }
    \end{dictentry}
    \begin{dictentry}{mSiFR}{n.}
        \dictdef*{
            radiator, space heater
        }
    \end{dictentry}
    \begin{dictentry}{inSiFR}{n.}
        \dictdef*{

        }
    \end{dictentry}
    \begin{dictentry}{SuliFR}{n.}
        \dictdef{
            body temperature
        }
        \dictdef{
            warm-bloodedness
        }
    \end{dictentry}
    \begin{dictentry}{SasiFR}{n.}
        \dictdef*{
            matchstick
        }
    \end{dictentry}
    \begin{dictentry}{SidiFR}{n.}
        \dictdef{
            sand
        }
    \end{dictentry}
    \begin{dictentry}{aSiFRu}{n.}
        \dictdef*{
            sauna
        }
    \end{dictentry}
    \begin{dictentry}{SuFRi}{n., adj.}
        \dictdef*{
            dark orange, red-orange
        }
    \end{dictentry}
    \begin{dictentry}{uSiFRi}{adj.}
        \dictdef*{
            feverish, having an elevated body temperature
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{s}{h}
    \begin{dictentry}{SaH}{n.}
        \dictdef*{a foul smell, a pungent odor}
    \end{dictentry}
    \begin{dictentry}{SiyaH}{v.tr.}
        \dictdef*{to stink, to smell bad, to be malodorous}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{s}{j}
    \begin{dictentry}{SaJ}{n.}
        \dictdef*{
            sleep, slumber, the state of being asleep
        }
    \end{dictentry}
    \begin{dictentry}{SiiY}{v.tr.}
        \dictdef*{
            to say good-bye to \textit{sme.}, to bid adieu
        }
    \end{dictentry}
    \begin{dictentry}{SiyaJ}{v.intr.}
        \dictdef*{
            to sleep, to be asleep, to fall asleep
        }
    \end{dictentry}
    \begin{dictentry}{iSaaJ}{v.intr.}
        \dictdef*{
            to go to bed, to relax with the intention of falling asleep    
        }
    \end{dictentry}
    \begin{dictentry}{SiSiyaJ}{v.tr.}
        \dictdef{
            to put to sleep, to knock out
        }
        \dictdef{
            \textit{(fig.)} to bore \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaSiY}{v.tr.}
        \dictdef{
            to put \textit{sme.} to bed, to tuck \textit{sme.} in
        }
        \dictdef{
            to coddle \textit{sme.}, patronize \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{SaJa}{adj.}
        \dictdef{
            tiring, sleep-inducing
        }
        \dictdef{
            evening's, in the evening \textit{(from \famword{SaJa-TaN})}
        }
        \dictdef{
            \textit{(fig.)} boring
        }
    \end{dictentry}
    \begin{dictentry}{SurYi}{n.}
        \dictdef*{
            pillow
        }
    \end{dictentry}
    \begin{dictentry}{SarYi}{n.}
        \dictdef*{
            a warm drink drunk before bed, nightcap
        }
    \end{dictentry}
    \begin{dictentry}{iSuJa}{n.}
        \dictdef{
            bed
        }
        \dictdef{
            bedroom
        }
    \end{dictentry}
    \begin{dictentry}{mSiY}{n.}
        \dictdef*{
            sedative, sleeping pill, sleep aid
        }
    \end{dictentry}
    \begin{dictentry}{inSiY}{n.}
        \dictdef*{
            nap, catnap
        }
    \end{dictentry}
    \begin{dictentry}{SuliY}{n.}
        \dictdef*{
            back, dorsum, the human back
        }
    \end{dictentry}
    \begin{dictentry}{SuJu}{n.}
        \dictdef*{
            bat
        }
    \end{dictentry}
    \begin{dictentry}{SajuJa}{n.}
        \dictdef{
            quilt, comforter, blanket, duvet
        }
        \dictdef{
            sleeping bag
        }
    \end{dictentry}
    \begin{dictentry}{SidiY}{n.}
        \dictdef*{
            rheum, sleep sand, eye booger, the crust or mucus that accumulates at the corner of one's eye during sleep
        }
    \end{dictentry}
    \begin{dictentry}{SimiYu}{n.}
        \dictdef*{
            crib, cradle, bassonet
        }
    \end{dictentry}
    \begin{dictentry}{SuuJ}{n.}
        \dictdef*{
            Dreamland, the world where people's souls go when they sleep
        }
    \end{dictentry}
    \begin{dictentry}{SuYi}{adj., n.}
        \dictdef*{
            the colors you see when you close your eyes
        }
    \end{dictentry}
    \begin{dictentry}{uSiYi}{adj.}
        \dictdef*{
            sleepy, tired, exhausted
        }
    \end{dictentry}
    \begin{dictentry}{SaJejalaj}{n.}
        \dictdef*{
            pajamas, sleep clothes
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{SaJanara}{int.}
        \dictdef*{
            good night, sleep well, sweet dreams, goodbye (when the speaker does not expect to see the addressee again until at least after one of them has had a night's sleep)
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{s}{n}
    % clean, healthy
    \begin{dictentry}{SaN}{n.}
        \dictdef{
            health
        }
        \dictdef{
            hygiene
        }
    \end{dictentry}
    \begin{dictentry}{SiiN}{v.tr.}
        \dictdef*{
            to clean \textit{smth.} or \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{SiyaN}{v.intr.}
        \dictdef{
            to be rinsed off of something, to be cleaned off of something
        }
        \dictdef{
            \textit{(of an illness)} to be cured, alleviated
        }
    \end{dictentry}
    \begin{dictentry}{iSaaN}{v.intr.}
        \dictdef{
            to clean up, to wash, to tidy up
        }
        \dictdef{
            to clean oneself, to bathe, to wash up
        }
    \end{dictentry}
    \begin{dictentry}{SiSiyaN}{v.tr.}
        \dictdef{
            to wash \textit{smth.} off of an object
        }
        \dictdef{
            to cure \textit{sme.} of an illness
        }
    \end{dictentry}
    \begin{dictentry}{aaSiN}{v.tr.}
        \dictdef*{
            to clean up after \textit{sme.}, to take care of someone in the capacity of a home nurse or caretaker
        }
    \end{dictentry}
    \begin{dictentry}{SaNa}{adj.}
        \dictdef{
            clean
        }
        \dictdef{
            healthy
        }
    \end{dictentry}
    \begin{dictentry}{SanaN}{n.}
        \dictdef*{
            maid, caretaker, home nurse
        }
    \end{dictentry}
    \begin{dictentry}{SurNi}{n.}
        \dictdef*{
            sponge
        }
    \end{dictentry}
    \begin{dictentry}{SarNi}{n.}
        \dictdef{
            soap, detergent
        }
        \dictdef{
            liquid medicine
        }
    \end{dictentry}
    \begin{dictentry}{iSuNa}{n.}
        \dictdef*{
            bathroom
        }
    \end{dictentry}
    \begin{dictentry}{mSiN}{n.}
        \dictdef{
            syringe
        }
        \dictdef{
            vaccine
        }
    \end{dictentry}
    \begin{dictentry}{inSiN}{n.}
        \dictdef*{
            pick-me-up, remedy
        }
    \end{dictentry}
    \begin{dictentry}{SuliN}{n.}
        \dictdef*{
            spleen
        }
    \end{dictentry}
    \begin{dictentry}{SuNu}{n.}
        \dictdef*{
            ladybug, believed to grant good health to anyone in lands on
        }
    \end{dictentry}
    \begin{dictentry}{SasiN}{n.}
        \dictdef*{
            some kinda healthy plant idk
        }
    \end{dictentry}
    \begin{dictentry}{SajuNa}{n.}
        \dictdef*{
            washcloth
        }
    \end{dictentry}
    \begin{dictentry}{SidiN}{n.}
        \dictdef*{
            medicine
        }
    \end{dictentry}
    \begin{dictentry}{aSiNu}{n.}
        \dictdef{
            dishwasher
        }
        \dictdef{
            washing machine
        }
    \end{dictentry}
    \begin{dictentry}{SimiNu}{n.}
        \dictdef{
            wash basin, sink, bathtub
        }
    \end{dictentry}
    \begin{dictentry}{SuNi}{n., adj.}
        \dictdef*{
            healthy glow to one's skin, looking healthy
        }
    \end{dictentry}
    \begin{dictentry}{uSiNi}{adj.}
        \dictdef*{
            feeling healthy after a period of illness
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{SaNaarjan}{n.}
        \dictdef*{
            doctor
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{s}{r}
    % identical, same
    \begin{dictentry}{SaR}{n.}
        \dictdef{
            identity
        }
        \dictdef{
            equal
        }
    \end{dictentry}
    \begin{dictentry}{SiiR}{v.tr.}
        \dictdef*{
            to equal, be the same as, 
        }
    \end{dictentry}
    \begin{dictentry}{SiyaR}{v.intr.}
        \dictdef*{
            to equal, be equal, be the same as
        }
    \end{dictentry}
    \begin{dictentry}{iSaaR}{v.intr.}
        \dictdef*{
            to equate oneself with, to identify as
        }
    \end{dictentry}
    \begin{dictentry}{SiSiyaR}{v.tr.}
        \dictdef*{
            to identify \textit{smth.} or \textit{sme.}, assign an identity to \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaSiR}{v.tr.}
        \dictdef*{
            to recruit \textit{sme.}, convert \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{SaRa}{adj.}
        \dictdef*{
            identical, same
        }
    \end{dictentry}
    \begin{dictentry}{SanaR}{n.}
        \dictdef{
            recruit, convert
        }
        \dictdef{
            private, most junior rank of military personnel
        }
        \dictdef{
            dictator, monarch, totalitarian leader of a state or kingdom
        }
    \end{dictentry}
    \begin{dictentry}{SurRi}{n.}
        \dictdef*{
            duplicate
        }
    \end{dictentry}
    \begin{dictentry}{iSuRa}{n.}
        \dictdef*{
            totalitarion regime, dictatorship, absolute monarchy
        }
    \end{dictentry}
    \begin{dictentry}{mSiR}{n.}
        \dictdef*{
            identity documentation
        }
    \end{dictentry}
    \begin{dictentry}{inSiR}{n.}
        \dictdef*{
            resemblance
        }
    \end{dictentry}
    \begin{dictentry}{SuliR}{n.}
        \dictdef{
            fingerprint
        }
        \dictdef{
            \textit{(compounded with other body parts)} unique natural pattern on one's bodypart
        }
    \end{dictentry}
    \begin{dictentry}{SuRu}{n.}
        \dictdef*{
            naturally camouflaged animal
        }
    \end{dictentry}
    \begin{dictentry}{SasiR}{n.}
        \dictdef{
            signpost
        }
        \dictdef{
            more specific i7u7a thing?
        }
    \end{dictentry}
    \begin{dictentry}{SajuRa}{n.}
        \dictdef*{
            paper copy, paper scan, fax
        }
    \end{dictentry}
    \begin{dictentry}{aSiRu}{n.}
        \dictdef*{
            category
        }
    \end{dictentry}
    \begin{dictentry}{SimiRu}{n.}
        \dictdef*{
            type, kind, sort
        }
    \end{dictentry}
    \begin{dictentry}{SuRi}{n., adj.}
        \dictdef*{
            camouflage, camouflaged
        }
    \end{dictentry}
    \begin{dictentry}{uSiRi}{adj.}
        \dictdef*{
            in agreement, of the same opinion, from the same perspective
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{s}{w}
    % grandparent-grandchild (close)
    \begin{dictentry}{SanaW}{n.}
        \dictdef{
            grandparent
        }
        \dictdef{
            grandchild
        }
    \end{dictentry}
    \begin{dictentry}{aSiWu}{n.}
        \dictdef*{
            extended family, family including grandparents, aunts/uncles, cousins, etc.
        }
    \end{dictentry}
    \dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{aSiWuana}{n.}
        \dictdef*{a family member, a relative, a member of one's extended family}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sf}{r}
    %Swede, Sweden
    \begin{dictentry}{SFaR}{n.}
        \dictdef*{
            trouble, problem, hindrance, issue, bug
        }
    \end{dictentry}
    \begin{dictentry}{SFaRa}{adj.}
        \dictdef{
            troublesome, problematic
        }
        \dictdef{
            Swedish\\
            \textit{NB: though the sf--r meaning `Sweden,' is etymologically unrelated to the sf--r root meaning `trouble,' their homophony is often exploited for wordplay.}
        }
    \end{dictentry}
    \begin{dictentry}{SFurRi}{n.}
        \dictdef*{
            rutabaga, Swede, yellow turnip, Swedish turnip, the root of \textit{Brassica napus}
        }
    \end{dictentry}
    \begin{dictentry}{SFasiR}{n.}
        \dictdef*{
            rutabaga greens, the leaves of \textit{Brassica napus}
        }
    \end{dictentry}
    \begin{dictentry}{SFuuR}{n.}
        \dictdef*{
            the Swedish people\\
            \textit{from Old Norse \emph{svar}}
        }
    \end{dictentry}
    \begin{dictentry}{SFaRia}{n.}
        \dictdef*{
            Sweden
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sh}{n}
    \begin{dictentry}{SHaNa}{adj.}
        \dictdef*{
            English, of or related to England
        }
    \end{dictentry}
    \begin{dictentry}{SHuuN}{n.}
        \dictdef*{
            England, the English\\
            \textit{from Proto-Germanic \emph{\*sahs} `Saxon' via Middle Irish \emph{Saxain}}
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sk}{l}
    %learn, study
    \begin{dictentry}{SKaL}{n.}
        \dictdef*{
            learning, education, knowledge
        }
    \end{dictentry}
    \begin{dictentry}{SKiiL}{v.tr.}
        \dictdef*{
            to learn \textit{smth.}, to study \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{SKiyaL}{v.intr.}
        \dictdef*{
            \textit{(of a subject)} to be taught, be studied, to be researched
        }
    \end{dictentry}
    \begin{dictentry}{iSKaaL}{v.intr.}
        \dictdef*{
            to study, to perform research, to learn
        }
    \end{dictentry}
    \begin{dictentry}{SKiSKiyaL}{v.tr.}
        \dictdef*{
            to teach \textit{smth.}, to instruct about \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaSKiL}{v.tr.}
        \dictdef*{
            to teach \textit{sme.}, to instruct \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{SKaLa}{adj.}
        \dictdef{
            educational, of or relating to education
        }
        \dictdef{
            instructive, aiding study
        }
        \dictdef{
            \textit{(of a person)} studious
        }
    \end{dictentry}
    \begin{dictentry}{SKanaL}{n.}
        \dictdef*{
            student, pupil
        }
    \end{dictentry}
    \begin{dictentry}{iSKuLa}{n.}
        \dictdef*{
            school
        }
    \end{dictentry}
    \begin{dictentry}{mSKiL}{n.}
        \dictdef*{
            notebook
        }
    \end{dictentry}
    \begin{dictentry}{inSKiL}{n.}
        \dictdef*{
            class, course
        }
    \end{dictentry}
    \begin{dictentry}{SKuliL}{n.}
        \dictdef*{
            the mind, the intellect
        }
    \end{dictentry}
    \begin{dictentry}{SKuLu}{n.}
        \dictdef*{
            dolphin
        }
    \end{dictentry}
    \begin{dictentry}{SKasiL}{n.}
        \dictdef*{
            pointer
        }
    \end{dictentry}
    \begin{dictentry}{SKajuLa}{n.}
        \dictdef{
            blackboard, chalkboard
        }
        \dictdef{
            whiteboard, dry-eraseboard
        }
    \end{dictentry}
    \begin{dictentry}{SKidiL}{n.}
        \dictdef*{
            fact
        }
    \end{dictentry}
    \begin{dictentry}{aSKiLu}{n.}
        \dictdef{
            textbook
        }
        \dictdef{
            scientific paper
        }
    \end{dictentry}
    \begin{dictentry}{SKimiLu}{n.}
        \dictdef*{
            lecture, talk, presentation
        }
    \end{dictentry}
    \begin{dictentry}{uSKiLi}{adj.}
        \dictdef*{
            arrogant in the form of perceived superior intellect
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{aaSKiLana}{n.}
        \dictdef*{
            teacher, lecturer
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sk}{nd}
    % Scandinavian, Norse, North Germanic
    \begin{dictentry}{SKaNDa}{adj.}
        \dictdef*{
            Scandinavian, Nordic, North Germanic
        }
    \end{dictentry}
    \begin{dictentry}{SKanaND}{n.}
        \dictdef*{
            Scandinavian person, person from the Nordic countries, Northern European, North Germanic
        }
    \end{dictentry}
    \begin{dictentry}{iSKuNDa}{n.}
        \dictdef{
            Scandinavia, the Scandinavian peninsula, the Nordic countries
        }
    \end{dictentry}
    \begin{dictentry}{SKuuND}{n.}
        \dictdef*{
            Scandinavian people, people from Nordic countries, Northern Europeans, North Germanic peoples (as a monolith)
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sl}{s}
    \begin{dictentry}{SLaS}{n.}
        \dictdef*{security, safety}
    \end{dictentry}
    \begin{dictentry}{SLiiS}{v.tr.}
        \dictdef*{to shut \emph{smth.} inside a container or behind a door}
    \end{dictentry}
    \begin{dictentry}{SLiyaS}{v.intr.}
        \dictdef{to be closed, to be locked}
        \dictdef{
            to be pickled, ferment in brine or vinegar
        }
    \end{dictentry}
    \begin{dictentry}{iSLaaS}{v.intr.}
        \dictdef{to lock oneself up, to shut oneself in, to close oneself away}
        \dictdef{to seclude oneself, to isolate onself, to cloister oneself}
    \end{dictentry}
    \begin{dictentry}{SLiSLiyaS}{v.tr.}
        \dictdef{to close, to shut, to lock}
        \dictdef{to pickle \textit{smth.}}
    \end{dictentry}
    \begin{dictentry}{aaSLiS}{v.tr.}
        \dictdef{to lock \textit{sme.} up, to shut \textit{sme.} in}
        \dictdef{to seclude \textit{sme.}, to isolate \textit{sme.}from others}
    \end{dictentry}
    \begin{dictentry}{SLaSa}{adj.}
        \dictdef*{secured, contained, safe}
    \end{dictentry}
    \begin{dictentry}{SLanaS}{n.}
        \dictdef{security guard}
        \dictdef{bank teller}
    \end{dictentry}
    \begin{dictentry}{SLurSi}{n.}
        \dictdef*{lock}
    \end{dictentry}
    \begin{dictentry}{SLarSi}{n.}
        \dictdef{
            brine, vinegar, liquid used in pickling 
        }
    \end{dictentry}
    \begin{dictentry}{iSLuSa}{n.}
        \dictdef{fortress}
        \dictdef{saferoom}
    \end{dictentry}
    \begin{dictentry}{mSLiS}{n.}
        \dictdef*{key}
    \end{dictentry}
    \begin{dictentry}{SLasiS}{n.}
        \dictdef*{zipper}
    \end{dictentry}
    \begin{dictentry}{SLajuSa}{n.}
        \dictdef{door, trap door, gate}
        \dictdef{tarp or other similar object used to close something off}
    \end{dictentry}
    \begin{dictentry}{SLidiS}{n.}
        \dictdef{
            salt
        }
    \end{dictentry}
    \begin{dictentry}{aSLiSu}{n.}
        \dictdef*{safe, lockbox, vault}
    \end{dictentry}
    \begin{dictentry}{SLimiSu}{n.}
        \dictdef*{a fenced-in area, an area contained by a fence}
    \end{dictentry}
    \begin{dictentry}{uSLiSi}{adj.}
        \dictdef{\textit{(of a person)} closed-off, repressed, reserved}
        \dictdef{confined, depressed, feeling trapped}
    \end{dictentry}
    \begin{dictentry}{SLuSaw}{n., adv.}
        \dictdef{
            north
        }
        \dictdef{
            northwards, to the north, in the north
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sn}{m}
    \begin{dictentry}{SNaMa}{adj.}
        \dictdef*{
            tasty, delicious, good to eat, good-tasting
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{sw}{t}
    %Swiss, Switzerland
    \begin{dictentry}{iSWuTa}{n.}
        \dictdef*{
            Switzerland
        }
    \end{dictentry}
    \begin{dictentry}{SWuuT}{n.}
        \dictdef*{
            the Swiss people
        }
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    T
%%%%%%%%%%%
\section*{T}

\begin{dictroot}{t}{fr}
    % parent-child (distance)
    \begin{dictentry}{TanaFR}{n.}
        \dictdef{
            parent considered less close due to not being biologically related or other reason (e.g., stepparent, parent-in-law, etc.)
        }
        \dictdef{
            child considered less close due to not being biologically related or other reason (e.g., stepchild, child-in-law, etc.)
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{t}{h}
    %Germany
    \begin{dictentry}{TaHa}{adj.}
        \dictdef*{
            German
        }
    \end{dictentry}
    \begin{dictentry}{TuuH}{n.}
        \dictdef{
            Germany
        }
        \dictdef{
            the German people
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{t}{k}
    % useful, to use, busy
    \begin{dictentry}{TiiK}{v.tr.}
        \dictdef*{
            to use \textit{smth.}, to benefit from \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{TiyaK}{v.intr.}
        \dictdef*{
            to be useful, to be of use, to come in handy, to benefit
        }
    \end{dictentry}
    \begin{dictentry}{iTaaK}{v.intr.}
        \dictdef*{
            to make oneself useful
        }
    \end{dictentry}
    \begin{dictentry}{TiTiyaK}{v.tr.}
        \dictdef{
            to set up, to put to use
        }
        \dictdef{
            to put into practice
        }
        \dictdef{
            to renovate, to repair, to refurbish
        }
    \end{dictentry}
    \begin{dictentry}{aaTiK}{v.tr.}
        \dictdef*{to manage \textit{sme.}, to boss \textit{sme.} around, to motive \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{TaKa}{adj.}
        \dictdef*{
            useful, helpful, beneficial
        }
    \end{dictentry}
    \begin{dictentry}{TanaK}{n.}
        \dictdef*{
            butler, maid, housekeeper
        }
    \end{dictentry}
    \begin{dictentry}{iTuKa}{n.}
        \dictdef*{
            job site, workplace
        }
    \end{dictentry}
    \begin{dictentry}{mTiK}{n.}
        \dictdef*{
            tool, instrument
        }
    \end{dictentry}
    \begin{dictentry}{TuKu}{n.}
        \dictdef*{
            beast of burden
        }
    \end{dictentry}
    \begin{dictentry}{uTiKi}{adj.}
        \dictdef*{busy, hard at work}
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{t}{lw}
    \begin{dictentry}{\famword{TaLW}}{n.}
        \dictdef{
            the land, like, as an idea
        }
        \dictdef{
            job, labor, employment
        }
    \end{dictentry}
    \begin{dictentry}{TiiLW}{v.tr.}
        \dictdef{
            to dig \textit{smth.} up, to unearth
        }
        \dictdef{
            to till \textit{smth.}, to plow \textit{smwh.}
        }
        \dictdef{
            to discover \textit{smth.}, to unearth \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{TiyaLW}{v.intr.}
        \dictdef{
            to be unearthed, to be unburied
        }
        \dictdef{
            to lie in the ground, to be buried, to be underground
        }
        \dictdef{
            to be discovered, to be found out
        }
        \dictdef{
            to be agreed upon, to be mutually accepted
        }
    \end{dictentry}
    \begin{dictentry}{iTaaLW}{v.intr.}
        \dictdef{
            to till, plow a field
        }
        \dictdef{
            to dig
        }
        \dictdef{
            to work, especially manual labor
        }
        \dictdef{
            to come to an agreement
        }
    \end{dictentry}
    \begin{dictentry}{TiTiyaLW}{v.tr.}
        \dictdef{
            to bury \textit{smth.}
        }
        \dictdef{
            to come to an agreement on \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaTiLW}{v.tr.}
        \dictdef{
            to drive or stick \textit{smth.} into the ground
        }
        \dictdef{
            to hire, to employ \textit{sme.} 
        }
    \end{dictentry}
    \begin{dictentry}{TaLWa}{adj.}
        \dictdef{
            earthly, not of heavenly or extraterrestrial quality
        }
        \dictdef{
            regular, ordinary, every-day, humdrum
        }
    \end{dictentry}
    \begin{dictentry}{TanaLW}{n.}
        \dictdef{
            farmer
        }
        \dictdef{
            employee, worker
        }
        \dictdef{
            groundskeeper, gardener
        }
    \end{dictentry}
    \begin{dictentry}{TurLWi}{n.}
        \dictdef*{
            potato
        }
    \end{dictentry}
    \begin{dictentry}{TarLWi}{n.}
        \dictdef*{
            mud
        }
    \end{dictentry}
    \begin{dictentry}{iTuLWa}{n.}
        \dictdef*{
            piece/section of land
        }
    \end{dictentry}
    \begin{dictentry}{mTiLW}{n.}
        \dictdef*{
            spade, shovel
        }
    \end{dictentry}
    \begin{dictentry}{inTiLW}{n.}
        \dictdef*{
            island
        }
    \end{dictentry}
    \begin{dictentry}{TuLWu}{n.}
        \dictdef*{
            mole
        }
    \end{dictentry}
    \begin{dictentry}{TasiLW}{n.}
        \dictdef{
            hill, mound
        }
        \dictdef{
            worm
        }
    \end{dictentry}
    \begin{dictentry}{TajuLWa}{n.}
        \dictdef{
            the ground, soil
        }
        \dictdef{
            topsoil
        }
        \dictdef{
            field, cultivated land
        }
        \dictdef{
            forest floor
        }
    \end{dictentry}
    \begin{dictentry}{TidiLW}{n.}
        \dictdef*{
            actual dirt
        }
    \end{dictentry}
    \begin{dictentry}{aTiLWu}{n.}
        \dictdef*{
            grave, burial pit
        }
    \end{dictentry}
    \begin{dictentry}{TimiLWu}{n.}
        \dictdef*{
            valley
        }
    \end{dictentry}
    \begin{dictentry}{TuLWi}{n., adj.}
        \dictdef*{
            brown, the color brown
        }
    \end{dictentry}
    \begin{dictentry}{usTaLW}{n.}
        \dictdef*{
            jeans, denim pants, work pants
        }
    \end{dictentry}
    \begin{dictentry}{TuLWaw}{n., adv.}
        \dictdef{
            the right hand
        }
        \dictdef{
            to the right, on the right side
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{t}{t}
    % young, new
    \begin{dictentry}{TaT}{n.}
        \dictdef{
            news
        }
        \dictdef{
            youth
        }
    \end{dictentry}
    \begin{dictentry}{TiiT}{v.tr.}
        \dictdef*{
            to introduce, debut \textit{smth.} or \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{TiyaT}{v.intr.}
        \dictdef{
            to be introduced, debut, begin
        }
    \end{dictentry}
    \begin{dictentry}{iTaaT}{v.intr.}
        \dictdef{
            to introduce oneself
        }
        \dictdef{
            to involve oneself in an activity or event
        }
    \end{dictentry}
    \begin{dictentry}{TaTa}{adj.}
        \dictdef{
            new, recent
        }
        \dictdef{
            young
        }
    \end{dictentry}
    \begin{dictentry}{TanaT}{n.}
        \dictdef{
            youngster, youth, teenager, adolescent
        }
        \dictdef{
            noob, newbie, new guy
        }
    \end{dictentry}
    \begin{dictentry}{TurTi}{n.}
        \dictdef*{
            piece of information
        }
    \end{dictentry}
    \begin{dictentry}{iTuTa}{n.}
        \dictdef{
            frontier
        }
        \dictdef{
            \textit{(figuratively)} forefront
        }
    \end{dictentry}
    \begin{dictentry}{mTiT}{n.}
        \dictdef{
            technology, the accumulated tools of a culture
        }
        \dictdef{
            innovative, novel tool
        }
    \end{dictentry}
    \begin{dictentry}{inTiT}{n.}
        \dictdef*{
            gossip, hearsay
        }
    \end{dictentry}
    \begin{dictentry}{TuliT}{n.}
        \dictdef*{
            growth, cyst, tumor, cancer
        }
    \end{dictentry}
    \begin{dictentry}{TuTu}{n.}
        \dictdef*{
            some kind of vocal animal whose cry is symbolic or indicative of something
        }
    \end{dictentry}
    \begin{dictentry}{TasiT}{n.}
        \dictdef{
            conversation thread
        }
        \dictdef{
            timeline, newsfeed
        }
        \dictdef{
            chat channel
        }
    \end{dictentry}
    \begin{dictentry}{TajuTa}{n.}
        \dictdef*{
            newspaper
        }
    \end{dictentry}
    \begin{dictentry}{TidiT}{n.}
        \dictdef*{
            hint, small piece of information
        }
    \end{dictentry}
    \begin{dictentry}{aTiTu}{n.}
        \dictdef*{
            television or radio news broadcast
        }
    \end{dictentry}
    \begin{dictentry}{TuTi}{n., adj.}
        \dictdef*{
            black-and-white, monochrome
        }
    \end{dictentry}
    \begin{dictentry}{uTiTi}{adj.}
        \dictdef{
            inexperienced
        }
        \dictdef{
            overwhelmed due to inexperience
        }
    \end{dictentry}
    \begin{dictentry}{TaTjalaT}{n.}
        \dictdef{
            T-shirt
        }
    \end{dictentry}
    \begin{dictentry}{TuuT}{n.}
        \dictdef{
            culture and people group that is not ethnically Narelandic
        }
        \dictdef{
            \textit{(derogatory)} immigrants, refugees 
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{tr}{l}
    \begin{dictentry}{TRanaL}{n.}
        \dictdef*{troll, ogre}
    \end{dictentry}
\end{dictroot}

%%%%%%%%%%%
%    W
%%%%%%%%%%%
\section*{W}

\begin{dictroot}{w}{b}
    % to come, to come back
    \begin{dictentry}{WaB}{n.}
        \dictdef*{
            arrival, return, appearance
        }
    \end{dictentry}
    \begin{dictentry}{WiiB}{v.tr.}
        \dictdef*{
            to arrive \textit{smwh.}, attend \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{WiyaB}{v.intr.}
        \dictdef{
            \textit{(of an object)} to arrive, show up, appear
        }
        \dictdef{
            \textit{(of an object)} to return, come back to a place
        }
    \end{dictentry}
    \begin{dictentry}{iWaaB}{v.intr.}
        \dictdef{
            to arrive, show up, appear
        }
        \dictdef{
            to return, come back to a place
        }
    \end{dictentry}
    \begin{dictentry}{WiWiyaB}{v.tr.}
        \dictdef*{
            to deliver, bring, send, retrieve \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaWiB}{v.tr.}
        \dictdef{
            to guide, escort \textit{sme.}
        }
        \dictdef{
            to send, bring, retrieve \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{WaBa}{adj.}
        \dictdef*{
            recurring, returning, repeating
        }
    \end{dictentry}
    \begin{dictentry}{WanaB}{n.}
        \dictdef*{
            guest, regular
        }
    \end{dictentry}
    \begin{dictentry}{iWuBa}{n.}
        \dictdef{
            the arrivals section of a station, airport
        }
        \dictdef{
            foyer, entrance hall, lobby
        }
    \end{dictentry}
    \begin{dictentry}{WuBu}{n.}
        \dictdef*{
            migratory animal of some kind, gotta figure out
        }
    \end{dictentry}
    \begin{dictentry}{WasiB}{n.}
        \dictdef*{
            boomerang
        }
    \end{dictentry}
    \begin{dictentry}{WajuBa}{n.}
        \dictdef*{
            door mat, welcome mat
        }
    \end{dictentry}
    \begin{dictentry}{WidiB}{n.}
        \dictdef{
            \textit{(colloquial)} the first snow of the winter
        }
        \dictdef{
            \textit{(colloquial, poetic)} a period of snowfall during springtime, after the snow from winter has melted away
        }
    \end{dictentry}
    \begin{dictentry}{WuBi}{n.,adj.}
        \dictdef{
            reflection, mirror image
        }
        \dictdef{
            reflected, mirrored
        }
    \end{dictentry}
    \begin{dictentry}{uWiBi}{adj.}
        \dictdef{
            self-conscious, introspective
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{w}{h}
    % sex
    \begin{dictentry}{WaH}{n.}
        \dictdef*{
            sex
        }
    \end{dictentry}
    \begin{dictentry}{WiiH}{v.tr.}
        \dictdef*{
            to have sex with \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{WiyaH}{v.intr.}
        \dictdef*{
            to get off, experience sexual satisfaction, have an orgasm
        }
    \end{dictentry}
    \begin{dictentry}{iWaaH}{v.intr.}
        \dictdef*{
            to have sex
        }
    \end{dictentry}
    \begin{dictentry}{WiWiyaH}{v.tr.}
        \dictdef*{
            to get \textit{sme.} off, make \textit{sme.} orgasm
        }
    \end{dictentry}
    \begin{dictentry}{aaWiH}{v.tr.}
        \dictdef*{
            to seduce \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{WaHa}{adj.}
        \dictdef*{
            sexy, sexual
        }
    \end{dictentry}
    \begin{dictentry}{WanaH}{n.}
        \dictdef*{
            sexual partner
        }
    \end{dictentry}
    \begin{dictentry}{WarHi}{n.}
        \dictdef*{
            lubricant
        }
    \end{dictentry}
    \begin{dictentry}{mWiH}{n.}
        \dictdef*{
            sex toy
        }
    \end{dictentry}
    \begin{dictentry}{inWiH}{n.}
        \dictdef*{
            quickie, brief sexual encounter
        }
    \end{dictentry}
    \begin{dictentry}{WuliH}{n.}
        \dictdef*{
            genitals
        }
    \end{dictentry}
    \begin{dictentry}{WuHu}{n.}
        \dictdef*{
            masturbatory aid, fleshlight
        }
    \end{dictentry}
    \begin{dictentry}{WasiH}{n.}
        \dictdef*{
            penis
        }
    \end{dictentry}
    \begin{dictentry}{WidiH}{n.}
        \dictdef*{
            Viagra, Cialis, drug used to enhance sexual performance
        }
    \end{dictentry}
    \begin{dictentry}{aWiHu}{n.}
        \dictdef*{
            vagina
        }
    \end{dictentry}
    \begin{dictentry}{WimiHu}{n.}
        \dictdef*{
            condom
        }
    \end{dictentry}
    \begin{dictentry}{uWiHi}{adj.}
        \dictdef*{
            horny, sexually aroused
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{w}{l}
    % old, elderly
    % also to forget
    \begin{dictentry}{WaL}{n.}
        \dictdef{
            old age, seniority
        }
        \dictdef*{
            the distant past
        }
    \end{dictentry}
    \begin{dictentry}{WiiL}{v.tr.}
        \dictdef*{
            to forget \textit{smth.} from deep in one's memory, long ago
        }
    \end{dictentry}
    \begin{dictentry}{WiyaL}{v.intr.}
        \dictdef*{
            to get lost to time, be forgotten into legend
        }
    \end{dictentry}
    \begin{dictentry}{iWaaL}{v.intr.}
        \dictdef*{
            to forget, be forgetful
        }
    \end{dictentry}
    \begin{dictentry}{WiWiyaL}{v.tr.}
        \dictdef*{
            to surpress or censor \textit{smth.}, \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{aaWiL}{v.tr.}
        \dictdef*{
            to cause \textit{sme.} to feel the inevitable decay of age and senility
        }
    \end{dictentry}
    \begin{dictentry}{WaLa}{adj.}
        \dictdef{
            old, not recent
        }
        \dictdef{
            elderly
        }
    \end{dictentry}
    \begin{dictentry}{WanaL}{n.}
        \dictdef*{
            old person, senior citizen
        }
    \end{dictentry}
    \begin{dictentry}{iWuLa}{n.}
        \dictdef*{
            old times, the good old days
        }
    \end{dictentry}
    \begin{dictentry}{aWiLu}{n.}
        \dictdef*{
            retirement home
        }
    \end{dictentry}
    \begin{dictentry}{uWiLi}{adj.}
        \dictdef*{
            feeling old, decaying, fading
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{w}{w}
    \begin{dictentry}{WaW}{n.}
        \dictdef{
            sweetness, sugaryness
        }
        \dictdef{
            flirtation, flirtiness
        }
    \end{dictentry}
    \begin{dictentry}{WiiW}{v.tr.}
        \dictdef{
            to flirt with \textit{sme.}
        }
        \dictdef{
            to suck up to \textit{sme.}, to flatter \textit{sme.}
        }
    \end{dictentry}
    \begin{dictentry}{WiyaW}{v.intr.}
        \dictdef*{
            to be flattering or flirtatious
        }
        \dictdef*{
            \textit{(of an object, particularly clothes)} to be flattering, suit one's figure or style
        }
    \end{dictentry}
    \begin{dictentry}{iWaaW}{v.intr.}
        \dictdef*{
            to flirt, flatter
        }
    \end{dictentry}
    \begin{dictentry}{WiWiyaW}{v.tr.}
        \dictdef*{
            to interpret something as flattering
        }
    \end{dictentry}
    \begin{dictentry}{\famword{WaWa}}{adj.}
        \dictdef{
            sweet, sugary, saccharine
        }
        \dictdef{
            sweet, docile, lovely, adorable
        }
    \end{dictentry}
    \begin{dictentry}{WanaW}{n.}
        \dictdef*{
            dear, honey, sweetie, hon, sugar
        }
    \end{dictentry}
    \begin{dictentry}{\famword{WarWi}}{n.}
        \dictdef*{
            sweet drink, soft drink, sugary beverage
        }
    \end{dictentry}
    \begin{dictentry}{WuWu}{n.}
        \dictdef*{
            pet animal 
        }
    \end{dictentry}
    \begin{dictentry}{\famword{WidiW}}{n.}
        \dictdef*{
            sugar, powdered sweetener
        }
    \end{dictentry}
    \begin{dictentry}{uWiWi}{adj.}
        \dictdef*{
            flattered
        }
    \end{dictentry}
\dictsubtitle{Compounds \& Secondary Derivations}
    \begin{dictentry}{\famword{WarWibin}}{n.}
        \dictdef*{
            honey
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{wr}{p}
    %Europe
    %iWRuPa = continent
    %WRaPia = EU
    %WRuuP = white people?
    \begin{dictentry}{iWRuPa}{n.}
        \dictdef*{
            Europe
        }
    \end{dictentry}
    \begin{dictentry}{WRuuP}{n.}
        \dictdef*{
            \textit{(informal)} white people, Europeans
        }
    \end{dictentry}
    \begin{dictentry}{WRaPia}{n.}
        \dictdef*{
            \textit{(colloquial)} the European Union
        }
    \end{dictentry}
\end{dictroot}

\begin{dictroot}{ws}{n}
    % reason, happening
    \begin{dictentry}{WSaN}{n.}
        \dictdef{
            reason
        }
        \dictdef{
            cause
        }
    \end{dictentry}
    \begin{dictentry}{WeSiiN}{v.tr.}
        \dictdef*{
            to bring about, cause, effect
        }
    \end{dictentry}
    \begin{dictentry}{WeSiyaN}{v.intr.}
        \dictdef*{
            to happen, occur
        }
    \end{dictentry}
    \begin{dictentry}{iWSaaN}{v.tr.}
        \dictdef*{
            to do \textit{smth.}
        }
    \end{dictentry}
    \begin{dictentry}{aaWSiN}{v.tr.}
        \dictdef{
            to inspire, motivate, cause to act, coerce
        }
    \end{dictentry}
    \begin{dictentry}{WSaNa}{adj.}
        \dictdef*{
            current, relevant
        }
    \end{dictentry}
    \begin{dictentry}{WSanaN}{n.}
        \dictdef*{
            participant, actor
        }
    \end{dictentry}
    \begin{dictentry}{iWSuNa}{n.}
        \dictdef*{
            scene, place where something has happened or is happening
        }
    \end{dictentry}
    \begin{dictentry}{mWSiN}{n.}
        \dictdef*{
            method, manner
        }
    \end{dictentry}
    \begin{dictentry}{inWSiN}{n.}
        \dictdef*{
            excuse
        }
    \end{dictentry}
    \begin{dictentry}{uWSiNi}{adj.}
        \dictdef*{
            involved, invested
        }
    \end{dictentry}
\end{dictroot}

\end{multicols*}

\chapter{Rootless Words}
\begin{multicols*}{2}
\section{Verbs}
\begin{description}[leftmargin=*,labelwidth=*]
    \begin{dictentry}{dak}{mod.}
        \dictdef*{can, to be able to, to be allowed to}
    \end{dictentry}
    \begin{dictentry}{fidul}{asp.}
        \dictdef*{to be about to, to be going to}
    \end{dictentry}
    \begin{dictentry}{hak}{asp.}
        \dictdef*{to keep X-ing, to continue, to still X}
    \end{dictentry}
    \begin{dictentry}{hwii}{mod.}
        \dictdef*{not, no, don't, never}
    \end{dictentry}
    \begin{dictentry}{jaa}{asp.}
        \dictdef*{already, previously, by now}
    \end{dictentry}
    \begin{dictentry}{yin}{asp.}
        \dictdef*{just, recently, to have just done}
    \end{dictentry}
    \begin{dictentry}{kaj}{mod.}
        \dictdef*{to want, to want to}
    \end{dictentry}
    \begin{dictentry}{lit}{asp.}
        \dictdef*{to very, to do emphatically or to an extreme extent}
    \end{dictentry}
    \begin{dictentry}{naw}{asp.}
        \dictdef*{to stop, to cease, to quit}
    \end{dictentry}
    \begin{dictentry}{tuuq}{mod.}
        \dictdef*{to must, to have to}
    \end{dictentry}
    \begin{dictentry}{usnak}{mod.}
        \dictdef*{let it be so, \textit{(hortative)}}
    \end{dictentry}
    \begin{dictentry}{wadan}{asp.}
        \dictdef*{and now, but now, \textit{(stresses newness/recentness of the start of an eventuality)}}
    \end{dictentry}
\end{description}

\section{Postpositions}

\begin{description}[leftmargin=*,labelwidth=*]
    \begin{dictentry}{baj}{postp.}
        \dictdef*{using, by means of}
    \end{dictentry}
    \begin{dictentry}{bir}{postp.}
        \dictdef*{hanging from, suspended from}
    \end{dictentry}
    \begin{dictentry}{daw}{postp.}
        \dictdef*{to, towards}
    \end{dictentry}
    \begin{dictentry}{dis}{postp.}
        \dictdef*{because, because of, due to}
    \end{dictentry}
    \begin{dictentry}{fidul}{postp.}
        \dictdef*{before, in front of}
    \end{dictentry}
    \begin{dictentry}{fit}{postp.}
        \dictdef*{in, at, on}
    \end{dictentry}
    \begin{dictentry}{fun}{postp.}
        \dictdef*{from, out of}
    \end{dictentry}
    \begin{dictentry}{fus}{postp.}
        \dictdef*{at/in the home of}
    \end{dictentry}
    \begin{dictentry}{jan}{postp.}
        \dictdef*{under, beneath}
    \end{dictentry}
    \begin{dictentry}{yin}{postp.}
        \dictdef*{behind, after, in back of}
    \end{dictentry}
    \begin{dictentry}{lu}{postp.}
        \dictdef*{comprising, being from, being a subset of, being part of, \textit{(used for body parts and picking things out of a group)}}
    \end{dictentry}
    \begin{dictentry}{rijt}{postp.}
        \dictdef*{encircling, wrapped around, around}
    \end{dictentry}
    \begin{dictentry}{tui}{postp.}
        \dictdef*{on/covering the surface of}
    \end{dictentry}
    \begin{dictentry}{udan}{postp.}
        \dictdef*{if, depending on}
    \end{dictentry}
    \begin{dictentry}{uwa}{postp.}
        \dictdef*{over, above}
    \end{dictentry}
    \begin{dictentry}{wan}{postp.}
        \dictdef*{owned by, possessed by, 's, \textit{(indicates ownership or association)}}
    \end{dictentry}
\end{description}

\section{Attitudinals}

\begin{description}[leftmargin=*,labelwidth=*]
    \begin{dictentry}{x}{int.}
        \dictdef*{
            \textit{pronounced} \bripa{}\\
            \textit{expression of exasperation or mild disapproval}\\
            \textit{roughly equivalent to `smh'}
        }
    \end{dictentry}
    \begin{dictentry}{\textrm{X}}{int.}
        \dictdef*{
            \textit{pronounced} \bripa{} or \bripa{}\\
            \textit{expression of extreme annoyance, frustration, and disapproval}\\
            \textit{roughly equivalent to `ffs'}
        }
    \end{dictentry}
\end{description}

\section{Others}

\begin{description}[leftmargin=*, labelwidth=*]
    \begin{dictentry}{carde}{}
        \dictdef*{
            sir, milord, sire, boss, ma'am, milady
            }
    \end{dictentry}
\end{description}
\vspace*{\fill}
Number of Words Currently in Dictionary: \thedictwordcount
\end{multicols*}

\newpage

\section{Numbers}

\begin{multicols*}{2}
    \subsection{Cardinal Numbers}
    \begin{description}[align=parrightcent,leftmargin=!,labelwidth=4cm]
        \item[sar] one
        \item[\phantom{b}pas] two
        \item[\phantom{p}bar] three
        \item[qad] four
        \item[kaj] five
        \item[sesar] six
        \item[\phantom{b}pepas] seven
        \item[\phantom{p}bebar] eight
        \item[qeqad] nine
        \item[kekaj] ten
        \item[kekaj sar] eleven
        \item[kekaj pas] twelve
        \item[kekaj bar] thirteen
        \item[kekaj qad] fourteen
        \item[barkaj] fifteen
        \item[barkaj sesar] sixteen
        \item[barkaj pepas] seventeen
        \item[barkaj bebar] eightteen
        \item[barkaj qeqad] nineteen
        \item[qadkaj] twenty\phantom{b}
        \item[...]
        \item[kajkaj] twenty-five
        \item[sesarkaj] thirty
        \item[pepaskaj] thirty-five
        \item[bebarkaj] forty
        \item[qeqadkaj] forty-five
        \item[\phantom{j}dam] fifty
        \item[dam kaj] fifty-five
        \item[dam kekaj] sixty
        \item[dam barkaj] sixty-five
        \item[...]
        \item[dam qeqadkaj qeqad] ninety-nine
        \item[\phantom{j}dedam] one hundred
        \item[...]
        \item[\phantom{j}bardam] 150
        \item[qadedam] 200
        \item[kajdam] 250
        \item[\phantom{j}sesardam] 300
        \item[pepasdam] 350
        \item[\phantom{j}bebardam] 400
        \item[qeqadedam] 450
        \item[jal] 500
        \item[jal dam] 550
        \item[jal dedam] 600
        \item[...]
        \item[jal qeqadedam qeqadkaj qeqad] 999
        \item[suusan] 1000
        \item[...]
        \item[\phantom{b}pasesuusan] 2000
        \item[\phantom{j}barsuusan] 3000
        \item[qadsuusan] 4000
        \item[kajsuusan] 5000
        \item[sesarsuusan] 6000
        \item[\phantom{b}pepasesuusan] 7000
        \item[\phantom{j}bebarsuusan] 8000
        \item[qeqadsuusan] 9000
        \item[kekajsuusan] 10.000
        \item[kekajsarsuusan] 11.000
        \item[kekajpasesuusan] 12.000
        \item[...]
        \item[miljan] 1.000.000
        \item[miljad] 1.000.000.000 (10$^{9}$)
        \item[biljan] 1.000.000.000.000 (10$^{12}$)
        \item[biljad] 10$^{15}$
        \item[triljan] 10$^{18}$
        \item[triljad] 10$^{21}$
        \item[kfadriljan] 10$^{24}$
        \item[kfadriljad] 10$^{27}$
        \item[kfintiljan] 10$^{30}$
        \item[kfintiljad] 10$^{33}$
    \end{description}

    \subsection{Fractions}

    Fractions are formed by treating the entire number as if it were a root in the \rootpart{}a\rootpart{} pattern, with the final `a' in the cardinal number treated as the `a' in the pattern. This pseudo-root is then put into the in\rootpart{}i\rootpart{} pattern. Some example fractions:
    \begin{description}[align=parright,leftmargin=!,labelwidth=3.8cm]
        \item[inpis] one-half
        \item[inbir] one-third
        \item[inqid] one-quarter
        \item[inkij] one-fifth
        \item[insesir] one-sixth
        \item[inpepis] one-seventh
        \item[inbebir] one-eighth
        \item[inqeqid] one-ninth
        \item[inkekij] one-tenth
        \item[inkekajsir] one-eleventh
        \item[inkekajpis] one-twelfth
        \item[...]
        \item[injaldamsesarkajpis] 1 / 582
        \item[...]
        \item[indedim] one-hundredth (10$^{-2}$)
        \item[insuusin] one-thousandth (10$^{-3}$)
        \item[inkekajsuusin] one-tenthousandth (10$^{-4}$)
        \item[inmiljin] one-millionth (10$^{-6}$)
        \item[etc.]
    \end{description}
    If one wishes to describe a fraction with something other than one in the numerator, one simply precedes the fractional numeral for the denominator with the cardinal form of the numerator. So, for instance, 355/113 would be said aloud as \textit{pepasdam kaj indedamkekajbir}.
    \vfill\null
\columnbreak
\subsection{Ordinal Numbers}

Ordinals are not distinguishes from cardinal numbers in any explicit morphological way. In contexts where ordinal numerals would be used in other languages, \lang{} uses either cardinal numberals or other adjectives/adverbs to describe the relationship.

\end{multicols*}